---
title: "Brachial_Long_Data"
author: "Matthew Maslow"
date: "2023-07-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

# Packages

```{r}
library(tidyverse)
```


# Read in data
```{r}
data <- read.csv("CSVdata.csv")
colnames(data)
```


# Brachial Long (BL)

```{r}
# BL
# n = 68
BLdata <- data %>%
  filter(Group_char == "BL")
```
```{r}
# readr::write_csv(BLdata, file = "~/Desktop/LifeSpan Data Work/BLdata.csv")
```

### Patient Demo:

###### age
```{r}
ageBL <- 
  BLdata %>% 
  summarise(Mean = mean(age),
            Median = median(age),
            Stan.Dev. = sd(age)
            )
ageBL %>% pander::pander()
```

###### ASA PS

```{r}
asa_psBL <- 
  BLdata %>% 
  summarise(Mean = mean(asaps),
            Median = median(asaps),
            Stan.Dev. = sd(asaps)
            )
asa_psBL %>% pander::pander()
```

###### gender

```{r}

# 1 <- Males
# 2 <- Females

genderBL <- 
  BLdata %>% 
  summarise(Mean = mean(gender),
            Median = median(gender),
            Stan.Dev. = sd(gender)
            )
genderBL %>% pander::pander()
```

###### weight

```{r}
weightBL<-
  BLdata %>%
  summarise(Mean = mean(weight),
            Median = median(weight),
            Stan.Dev. = sd(weight)
            )
weightBL %>% pander::pander()
```

###### height

```{r}
heightBL<-
  BLdata %>%
  summarise(Mean = mean(height),
            Median = median(height),
            Stan.Dev. = sd(height)
            )
heightBL %>% pander::pander()
```

###### bmi

```{r}
bmiBL <- 
  BLdata %>% 
  summarise(Mean = mean(bmi),
            Median = median(bmi),
            Stan.Dev. = sd(bmi)
            )
bmiBL %>% pander::pander()
```

###### bmiGE35

```{r}
bmiGE35BL <- 
  BLdata %>% 
  summarise(Mean = mean(bmiGE35),
            Median = median(bmiGE35),
            Stan.Dev. = sd(bmiGE35)
            )
bmiGE35BL %>% pander::pander()
```

###### bmiGE40

```{r}
bmiGE40BL <- 
  BLdata %>% 
  summarise(Mean = mean(bmiGE40),
            Median = median(bmiGE40),
            Stan.Dev. = sd(bmiGE40)
            )
bmiGE40BL %>% pander::pander()
```

### Prior History:

###### AF

```{r}
afBL <-
  BLdata %>%
  summarise(Mean = mean(af),
            Median = median(af),
            Stan.Dev. = sd(af)
            )
afBL %>% pander::pander()
```

###### DM

```{r}
dmBL <-
  BLdata %>%
  summarise(Mean = mean(dm),
            Median = median(dm),
            Stan.Dev. = sd(dm)
            )
dmBL %>% pander::pander()
```

###### CKD

```{r}
ckdBL <-
  BLdata %>%
  summarise(Mean = mean(ckd),
            Median = median(ckd),
            Stan.Dev. = sd(ckd)
            )
ckdBL %>% pander::pander()
```

###### HTN

```{r}
htnBL <-
  BLdata %>%
  summarise(Mean = mean(htn),
            Median = median(htn),
            Stan.Dev. = sd(htn)
            )
htnBL %>% pander::pander()
```

###### COPD

```{r}
copdBL <-
  BLdata %>%
  summarise(Mean = mean(copd),
            Median = median(copd),
            Stan.Dev. = sd(copd)
            )
copdBL %>% pander::pander()
```

###### Hyperlipidemia

```{r}
hyperlipidBL <-
  BLdata %>% 
  mutate(hyperlipid = parse_number(hyperlipid)) %>%
  summarise(Mean = mean(hyperlipid),
            Median = median(hyperlipid),
            Stan.Dev. = sd(hyperlipid)
            )
hyperlipidBL %>% pander::pander()
```

###### OSA

```{r}
osaBL <-
  BLdata %>%
  summarise(Mean = mean(osa),
            Median = median(osa),
            Stan.Dev. = sd(osa)
            )
osaBL %>% pander::pander()
```

###### PAD

```{r}
padBL <-
  BLdata %>%
  summarise(Mean = mean(pad),
            Median = median(pad),
            Stan.Dev. = sd(pad)
            )
padBL %>% pander::pander()
```

###### Total Num of Comorbidities

```{r}
totnum_comorbidBL <-
  BLdata %>%
  summarise(Mean = mean(totnum_comorbid),
            Median = median(totnum_comorbid),
            Stan.Dev. = sd(totnum_comorbid)
            )
totnum_comorbidBL %>% pander::pander()
```

### Surgery:

###### Group Variables

```{r}
surgeryinfoBL <- 
  BLdata %>% select(surgtype_char, surgtype)
surgeryinfoBL %>% pander::pander()
```

###### Surgery occurences

```{r}
surgFreqBL <- 
  surgeryinfoBL %>%
  summarise(Mean = mean(surgtype),
            Median = median(surgtype),
            Stan.Dev. = sd(surgtype)
            )
surgFreqBL %>% pander::pander()
```

### Intraop FLuids:

###### Crystalloid Use

```{r}
crystalloidBL <- 
  BLdata %>%
  summarise(Mean = mean(crystalloid),
            Median = median(crystalloid),
            Stan.Dev. = sd(crystalloid)
            )
crystalloidBL %>% pander::pander()
```

###### PRBC

```{r}
prbcBL <- 
  BLdata %>%
  summarise(Mean = mean(prbc),
            Median = median(prbc),
            Stan.Dev. = sd(prbc)
            )
prbcBL %>% pander::pander()
```

###### Autologous

```{r}
autologousBL <- 
  BLdata %>%
  summarise(Mean = mean(autologous),
            Median = median(autologous),
            Stan.Dev. = sd(autologous)
            )
autologousBL %>% pander::pander()
```

###### Total Num of Colloid Products

```{r}
totnum_colloidBL <- 
  BLdata %>%
  summarise(Mean = mean(totnum_colloid),
            Median = median(totnum_colloid),
            Stan.Dev. = sd(totnum_colloid)
            )
totnum_colloidBL %>% pander::pander()
```

###### Total Colloid Products (mls)

```{r}
totml_colloidBL <- 
  BLdata %>%
  summarise(Mean = mean(totml_colloid),
            Median = median(totml_colloid),
            Stan.Dev. = sd(totml_colloid)
            )
totml_colloidBL %>% pander::pander()
```

###### Cell Saver Volume Retained

```{r}
cellsaver_volBL <- 
  BLdata %>%
  summarise(Mean = mean(cellsaver_vol),
            Median = median(cellsaver_vol),
            Stan.Dev. = sd(cellsaver_vol)
            )
cellsaver_volBL %>% pander::pander()
```

###### Urine Output

```{r}
urineBL <- 
  BLdata %>%
  summarise(Mean = mean(urine),
            Median = median(urine),
            Stan.Dev. = sd(urine)
            )
urineBL %>% pander::pander()
```

### Surgical time:

###### CPB duration (min)

```{r}
cpbDurationBL <-
  BLdata %>%
  summarise(Mean = mean(cpb_duration),
            Median = median(cpb_duration),
            Stan.Dev. = sd(cpb_duration)
            )
cpbDurationBL %>% pander::pander()
  
```

###### Aortic Clamp time (min)

```{r}
aortic_clamp_timeBL <-
  BLdata %>%
  summarise(Mean = mean(aortic_clamp_time),
            Median = median(aortic_clamp_time),
            Stan.Dev. = sd(aortic_clamp_time)
            )
aortic_clamp_timeBL %>% pander::pander()
```

###### Ejection Fraction PRE (%)

```{r}
ef_preBL <-
  BLdata %>%
  mutate(EF_pre = parse_number(EF_pre)) %>%
  summarise(Mean = mean(EF_pre,na.rm = TRUE),
            Median = median(EF_pre, na.rm = TRUE),
            Stan.Dev. = sd(EF_pre, na.rm = TRUE)
            )
ef_preBL %>% pander::pander()
```

###### Ejection Fraction POST (%)

```{r}
ef_postBL <-
  BLdata %>%
  mutate(EF_post = parse_number(EF_post)) %>%
  summarise(Mean = mean(EF_post,na.rm = TRUE),
            Median = median(EF_post, na.rm = TRUE),
            Stan.Dev. = sd(EF_post, na.rm = TRUE)
            )
ef_postBL %>% pander::pander()
```



### Intra-Operative Meds:

###### IntraOp Norepinephrine

```{r}
intra_norepBL <- 
  BLdata %>%
  summarise(Mean = mean(Intra_norep),
            Median = median(Intra_norep),
            Stan.Dev. = sd(Intra_norep)
            )
intra_norepBL %>% pander::pander()
```

###### IntraOp Nitroglycerin

```{r}
intra_nitroBL <- 
  BLdata %>%
  summarise(Mean = mean(intra_nitro),
            Median = median(intra_nitro),
            Stan.Dev. = sd(intra_nitro)
            )
intra_nitroBL %>% pander::pander()
```

###### IntraOp Vasopressin

```{r}
intra_vasoBL <- 
  BLdata %>%
  summarise(Mean = mean(intra_vaso),
            Median = median(intra_vaso),
            Stan.Dev. = sd(intra_vaso)
            )
intra_vasoBL %>% pander::pander()
```

###### IntraOp Milrinone

```{r}
intra_milBL <- 
  BLdata %>%
  summarise(Mean = mean(intra_mil),
            Median = median(intra_mil),
            Stan.Dev. = sd(intra_mil)
            )
intra_milBL %>% pander::pander()
```

###### IntraOp Epinephrine

```{r}
intra_epiBL <- 
  BLdata %>%
  summarise(Mean = mean(intra_epi),
            Median = median(intra_epi),
            Stan.Dev. = sd(intra_epi)
            )
intra_epiBL %>% pander::pander()
```

###### IntraOp Phenylephrine

```{r}
intra_phenylBL <- 
  BLdata %>%
  summarise(Mean = mean(intra_phenyl),
            Median = median(intra_phenyl),
            Stan.Dev. = sd(intra_phenyl)
            )
intra_phenylBL %>% pander::pander()
```

### Post Bypass Meds:

###### IntraOp Norepinephrine

```{r}
intraPost_norepBL <- 
  BLdata %>%
  summarise(Mean = mean(post_norep),
            Median = median(post_norep),
            Stan.Dev. = sd(post_norep)
            )
intraPost_norepBL %>% pander::pander()
```

###### IntraOp Nitroglycerin

```{r}
intraPost_nitroBL <- 
  BLdata %>%
  summarise(Mean = mean(post_nitro),
            Median = median(post_nitro),
            Stan.Dev. = sd(post_nitro)
            )
intraPost_nitroBL %>% pander::pander()
```

###### IntraOp Vasopressin

```{r}
intraPost_vasoBL <- 
  BLdata %>%
  summarise(Mean = mean(post_vaso),
            Median = median(post_vaso),
            Stan.Dev. = sd(post_vaso)
            )
intraPost_vasoBL %>% pander::pander()
```

###### IntraOp Milrinone

```{r}
intraPost_milBL <- 
  BLdata %>%
  summarise(Mean = mean(post_mil),
            Median = median(post_mil),
            Stan.Dev. = sd(post_mil)
            )
intraPost_milBL %>% pander::pander()
```

###### IntraOp Epinephrine

```{r}
intraPost_epiBL <- 
  BLdata %>%
  summarise(Mean = mean(post_epi),
            Median = median(post_epi),
            Stan.Dev. = sd(post_epi)
            )
intraPost_epiBL %>% pander::pander()
```

###### IntraOp Phenylephrine

```{r}
intraPost_phenylBL <- 
  BLdata %>%
  summarise(Mean = mean(post_phenyl),
            Median = median(post_phenyl),
            Stan.Dev. = sd(post_phenyl)
            )
intraPost_phenylBL %>% pander::pander()
```

### Central Aortic Cannula Pressures:

###### syst_cacc_precpb

```{r}
caccSYSTpreBL <- 
  BLdata %>% 
  summarise(Mean = mean(syst_cacc_precpb,na.rm = TRUE),
            Median = median(syst_cacc_precpb,na.rm = TRUE),
            Standard_Deviation = sd(syst_cacc_precpb,na.rm = TRUE)
            )
caccSYSTpreBL %>% pander::pander()
```


###### map_cacc_precpb

```{r}
caccMAPpreBL <- 
  BLdata %>% 
  summarise(Mean = mean(map_pacc_precpb,na.rm = TRUE),
            Median = median(map_cacc_precpb,na.rm = TRUE),
            Standard_Deviation = sd(map_cacc_precpb,na.rm = TRUE)
            )
caccMAPpreBL %>% pander::pander()
```

###### syst_cacc_postcpb2

```{r}
caccSystTWOpostBL <- 
  BLdata %>%
  summarise(Mean = mean(syst_cacc_postcpb2, na.rm = TRUE),
            Median = median(syst_cacc_postcpb2, na.rm = TRUE),
            Standard_Deviation = sd(syst_cacc_postcpb2,na.rm = TRUE)
            )
caccSystTWOpostBL %>% pander::pander()
```

###### map_cacc_postcpb2

```{r}
caccMapTWOpostBL <- 
  BLdata %>%
  summarise(Mean = mean(map_cacc_postcpb2, na.rm = TRUE),
            Median = median(map_cacc_postcpb2, na.rm = TRUE),
            Standard_Deviation = sd(map_cacc_postcpb2,na.rm = TRUE)
            )
caccMapTWOpostBL %>% pander::pander()
```

###### syst_cacc_postcpb10

```{r}
caccSystTENpostBL <- 
  BLdata %>%
  summarise(Mean = mean(syst_cacc_postcpb10, na.rm = TRUE),
            Median = median(syst_cacc_postcpb10, na.rm = TRUE),
            Standard_Deviation = sd(syst_cacc_postcpb10,na.rm = TRUE)
            )
caccSystTENpostBL %>% pander::pander()
```

###### map_cacc_postcpb10

```{r}
caccMapTENpostBL <- 
  BLdata %>%
  summarise(Mean = mean(map_cacc_postcpb10, na.rm = TRUE),
            Median = median(map_cacc_postcpb10, na.rm = TRUE),
            Standard_Deviation = sd(map_cacc_postcpb10,na.rm = TRUE)
            )
caccMapTENpostBL %>% pander::pander()
```


### Peripheral Arterial Catheter Pressures:

#### First Time Frame: Pre

###### syst_pacc_precpb

```{r}
paccSYSTpreBL <- 
  BLdata %>% 
  summarise(Mean = mean(syst_pacc_precpb,na.rm = TRUE),
            Median = median(syst_pacc_precpb,na.rm = TRUE),
            Stan.Dev. = sd(syst_pacc_precpb,na.rm = TRUE)
            )
paccSYSTpreBL %>% pander::pander()
```

###### map_pacc_precpb

```{r}
paccMAPpreBL <- 
  BLdata %>% 
  summarise(Mean = mean(map_pacc_precpb,na.rm = TRUE),
            Median = median(map_pacc_precpb,na.rm = TRUE),
            Standard_Deviation = sd(map_pacc_precpb,na.rm = TRUE)
            )
paccMAPpreBL %>% pander::pander()
```

###### diast_pacc_precpb

```{r}
paccDIASTpreBL <- 
  BLdata %>% 
  mutate(diast_pacc_precpb = parse_number(diast_pacc_precpb)) %>%
  summarise(Mean = mean(diast_pacc_precpb,na.rm = TRUE),
            Median = median(diast_pacc_precpb,na.rm = TRUE),
            Standard_Deviation = sd(diast_pacc_precpb,na.rm = TRUE)
            )
paccDIASTpreBL %>% pander::pander()
```

###### wave_pacc_precpb

```{r}
paccWAVEpreBL <- 
  BLdata %>% 
  summarise(Mean = mean(wave_pacc_precpb,na.rm = TRUE),
            Median = median(wave_pacc_precpb,na.rm = TRUE),
            Standard_Deviation = sd(wave_pacc_precpb,na.rm = TRUE)
            )
paccWAVEpreBL %>% pander::pander()
```





#### Second Time Frame: 2-Min-Post:

###### syst_pacc_postcpb2

```{r}
paccSystTWOpostBL <- 
  BLdata %>%
  summarise(Mean = mean(syst_pacc_postcpb2, na.rm = TRUE),
            Median = median(syst_pacc_postcpb2, na.rm = TRUE),
            Standard_Deviation = sd(syst_pacc_postcpb2,na.rm = TRUE)
            )
paccSystTWOpostBL %>% pander::pander()
```

###### map_pacc_postcpb2

```{r}
paccMapTWOpostBL <- 
  BLdata %>%
  summarise(Mean = mean(map_pacc_postcpb2, na.rm = TRUE),
            Median = median(map_pacc_postcpb2, na.rm = TRUE),
            Standard_Deviation = sd(map_pacc_postcpb2,na.rm = TRUE)
            )
paccMapTWOpostBL %>% pander::pander()
```

###### wave_pacc_postcpb2

```{r}
paccWaveTWOpostBL <- 
  BLdata %>%
  summarise(Mean = mean(wave_pacc_postcpb2, na.rm = TRUE),
            Median = median(wave_pacc_postcpb2, na.rm = TRUE),
            Standard_Deviation = sd(wave_pacc_postcpb2,na.rm = TRUE)
            )
paccWaveTWOpostBL %>% pander::pander()
```



#### Third Time Frame: 10-Min-Post:

###### syst_pacc_postcpb10

```{r}
paccSystTENpostBL <- 
  BLdata %>% 
  mutate(syst_pacc_postcpb10 = parse_number(syst_pacc_postcpb10)) %>%
  summarise(Mean = mean(syst_pacc_postcpb10, na.rm = TRUE),
            Median = median(syst_pacc_postcpb10, na.rm = TRUE),
            Standard_Deviation = sd(syst_pacc_postcpb10,na.rm = TRUE)
            )
paccSystTENpostBL %>% pander::pander()
```

###### map_pacc_postcpb10

```{r}
paccMapTENpostBL <- 
  BLdata %>% 
  mutate(map_pacc_postcpb10 = parse_number(map_pacc_postcpb10)) %>%
  summarise(Mean = mean(map_pacc_postcpb10, na.rm = TRUE),
            Median = median(map_pacc_postcpb10, na.rm = TRUE),
            Standard_Deviation = sd(map_pacc_postcpb10,na.rm = TRUE)
            )
paccMapTENpostBL %>% pander::pander()
```

###### wave_pacc_postcpb10

```{r}
paccWaveTENpostBL <- 
  BLdata %>% 
  mutate(wave_pacc_postcpb10 = parse_number(wave_pacc_postcpb10)) %>%
  summarise(Mean = mean(wave_pacc_postcpb10, na.rm = TRUE),
            Median = median(wave_pacc_postcpb10, na.rm = TRUE),
            Standard_Deviation = sd(wave_pacc_postcpb10,na.rm = TRUE)
            )
paccWaveTENpostBL %>% pander::pander()
```




#### CICU:

###### syst_pacc_cicu

```{r}
paccSYSTcicuBL <- 
  BLdata %>% 
  mutate(syst_pacc_cicu = parse_number(syst_pacc_cicu)) %>%
  summarise(Mean = mean(syst_pacc_cicu, na.rm = TRUE),
            Median = median(syst_pacc_cicu, na.rm = TRUE),
            Standard_Deviation = sd(syst_pacc_cicu,na.rm = TRUE)
            )
paccSYSTcicuBL %>% pander::pander()
```

###### diast_pacc_cicu

```{r}
paccDIASTcicuBL <- 
  BLdata %>% 
  mutate(diast_pacc_cicu = parse_number(diast_pacc_cicu)) %>%
  summarise(Mean = mean(diast_pacc_cicu, na.rm = TRUE),
            Median = median(diast_pacc_cicu, na.rm = TRUE),
            Standard_Deviation = sd(diast_pacc_cicu,na.rm = TRUE)
            )
paccDIASTcicuBL %>% pander::pander()
```

###### map_pacc_cicu

```{r}
paccMAPcicuBL <- 
  BLdata %>% 
  mutate(map_pacc_cicu = parse_number(map_pacc_cicu)) %>%
  summarise(Mean = mean(map_pacc_cicu, na.rm = TRUE),
            Median = median(map_pacc_cicu, na.rm = TRUE),
            Standard_Deviation = sd(map_pacc_cicu,na.rm = TRUE)
            )
paccMAPcicuBL %>% pander::pander()
```

###### wave_pacc_cicu

```{r}
paccWAVEcicuBL <- 
  BLdata %>% 
  mutate(wave_pacc_cicu = parse_number(wave_pacc_cicu)) %>%
  summarise(Mean = mean(wave_pacc_cicu, na.rm = TRUE),
            Median = median(wave_pacc_cicu, na.rm = TRUE),
            Standard_Deviation = sd(wave_pacc_cicu,na.rm = TRUE)
            )
paccWAVEcicuBL %>% pander::pander()
```









