---
title: "Catheter_Use_Comparisons"
author: "Matthew Maslow"
date: "2023-09-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(BSDA)
```

# Group Statistics

*All three groups are in same sample*

## Hypothesis

$ H_o: P_G = 0$
$ H_a: P_G \not= 0$

## Population Statistics
```{r}
pG = 0.07537688 # 15/199
pNull = 0
sdG = 0.2647
nG = 199
```
```{r}
(zG = (pG - pNull) / (sdG/sqrt(nG)))
```

## P-Value
```{r}
2 * pnorm(abs(zG), lower.tail = FALSE)
```
*We reject H_o, accept H_a*



# Individual Statistics

## Brachial Long (BL)

### Hypothesis:

$ H_o: P_{BL}-P_G = 0 $
$ H_a: P_{BL}-P_G \not= 0 $

### BL Stats

```{r}
pBL = 0.04411765 # 3/68
sdBL = 0.1702
nBL = 68
```

```{r}
(zBL = (pBL - pG) / ( (pBL-pG) / sqrt((pG*(1-pG))/nBL) ))
```

### P-Value

```{r}
2 * pnorm(abs(zBL), lower.tail = FALSE)
```

*In comparison of the Brachial Long group to the whole group, we reject the alternative, and accept the null. Therefore, the BL group is not significantly different from the whole group.*


## Radial Long (RL)

### Hypothesis:

$ H_o: P_{RL}-P_G = 0 $
$ H_a: P_{RL}-P_G \not= 0 $

### RL Stats

```{r}
pRL = 0.03174603 # 2/63
sdRL = 0.2458
nRL = 63
```

```{r}
(zRL = (pRL - pG) / ( (pRL-pG) / sqrt((pG*(1-pG))/nRL) ))
```

### P-Value

```{r}
2 * pnorm(abs(zRL), lower.tail = FALSE)
```

*In comparison of the Radial Long group to the whole group, we reject the alternative, and accept the null. Therefore, the BL group is not significantly different from the whole group.*


## Radial Short (RS)

### Hypothesis:

$ H_o: P_{RS}-P_G = 0 $
$ H_a: P_{RS}-P_G \not= 0 $

### RS Stats

```{r}
pRS = 0.1470588 # 10/68
sdRS = 0.3414
nRS = 68
```

```{r}
(zRS = (pRS - pG) / ( (pRS-pG) / sqrt((pG*(1-pG))/nRS) ))
```

### P-Value

```{r}
2 * pnorm(abs(zRS), lower.tail = FALSE)
```

*In comparison of the Radial Short group to the whole group, we reject the alternative, and accept the null. Therefore, the BL group is not significantly different from the whole group.*



# Group Comparisons

## BL Vs. RL

### Hypothesis:

$ H_o: P_{BL} - P_{RL} = 0 $
$ H_a: P_{BL} - P_{RL} \not= 0 $

### Stats

```{r}
(zBLRL = (pBL-pRL) / sqrt( (sdBL^2/nBL) + (sdRL^2/nRL) ))
```

### P-Value

```{r}
2 * pnorm(abs(zBLRL), lower.tail = FALSE)
```

*There is NO difference between Brachial and Radial Long*



## BL Vs. RS

### Hypothesis:

$ H_o: P_{BL} - P_{RS} = 0 $
$ H_a: P_{BL} - P_{RS} \not= 0 $

### Stats

```{r}
(zBLRS = (pBL-pRS) / sqrt( (sdBL^2/nBL) + (sdRS^2/nRS) ))
```

### P-Value

```{r}
2 * pnorm(abs(zBLRS), lower.tail = FALSE)
```

*There is a difference between Brachial long and Radial short*



## RL Vs. RS

### Hypothesis:

$ H_o: P_{RL} - P_{RS} = 0 $
$ H_a: P_{RL} - P_{RS} \not= 0 $

### Stats

```{r}
(zRLRS = (pRL-pRS) / sqrt( (sdRL^2/nRL) + (sdRS^2/nRS) ))
```

### P-value

```{r}
2 * pnorm(abs(zRLRS), lower.tail = FALSE)
```

*There is a difference between Radial short and long*







