---
title: "BL,RL,RS Data Tests"
author: "Matthew Maslow"
date: "2023-07-08"
output:
  pdf_document: default
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Packages

```{r}
library(tidyverse)
```

# Read in data
```{r}
BLdata <- read.csv("BLdata.csv")
RLdata <- read.csv("RLdata.csv")
RSdata <- read.csv("RSdata.csv")
```

# Test's


### Brachial Long:

#### Pre

##### 1: CA_Syst - PA_Syst

```{r}

kruskal.test(x = BLdata$syst_cacc_precpb, g = BLdata$syst_pacc_precpb)
t.test(x = BLdata$syst_cacc_precpb, y = BLdata$syst_pacc_precpb)
```

##### 2: CA_MAP - PA_MAP

```{r}
kruskal.test(x = BLdata$map_cacc_precpb, g = BLdata$map_pacc_precpb)
t.test(x = BLdata$map_cacc_precpb, y = BLdata$map_pacc_precpb)
```


#### Post 2 Minutes

##### 3: CA_Syst - PA_Syst

```{r}
kruskal.test(x = BLdata$syst_cacc_postcpb2, g = BLdata$syst_pacc_postcpb2)
t.test(x = BLdata$syst_cacc_postcpb2, y = BLdata$syst_pacc_postcpb2)
```

##### 4: CA_MAP - PA_MAP

```{r}
kruskal.test(x = BLdata$map_cacc_postcpb2, g = BLdata$map_pacc_postcpb2)
t.test(x = BLdata$map_cacc_postcpb2, y = BLdata$map_pacc_postcpb2)
```

#### Post 10 Minutes

##### 5: CA_Syst - PA_Syst

```{r}
kruskal.test(x = BLdata$syst_cacc_postcpb10, g = BLdata$syst_pacc_postcpb10)
t.test(x = BLdata$syst_cacc_postcpb10, y = BLdata$syst_pacc_postcpb10)
```

##### 6: CA_MAP - PA_MAP

```{r}
kruskal.test(x = BLdata$map_cacc_postcpb10, g = BLdata$map_pacc_postcpb10)
t.test(x = BLdata$map_cacc_postcpb10, y = BLdata$map_pacc_postcpb10)
```


### Radial Long:

#### Pre

##### 7: CA_Syst - PA_Syst

```{r}
kruskal.test(x = RLdata$syst_cacc_precpb, g = RLdata$syst_pacc_precpb)
t.test(x = RLdata$syst_cacc_precpb, y = RLdata$syst_pacc_precpb)
```

##### 8: CA_MAP - PA_MAP

```{r}
kruskal.test(x = RLdata$map_cacc_precpb, g = RLdata$map_pacc_precpb)
t.test(x = RLdata$map_cacc_precpb, y = RLdata$map_pacc_precpb)
```


#### Post 2 Minutes

##### 9: CA_Syst - PA_Syst

```{r}
kruskal.test(x = RLdata$syst_cacc_postcpb2, g = RLdata$syst_pacc_postcpb2)
t.test(x = RLdata$syst_cacc_postcpb2, y = RLdata$syst_pacc_postcpb2)
```

##### 10: CA_MAP - PA_MAP

```{r}
kruskal.test(x = RLdata$map_cacc_postcpb2, g = RLdata$map_pacc_postcpb2)
t.test(x = RLdata$map_cacc_postcpb2, y = RLdata$map_pacc_postcpb2)
```

#### Post 10 Minutes

##### 11: CA_Syst - PA_Syst

```{r}
RLdata <- 
  RLdata %>% 
  mutate(syst_pacc_postcpb10 = parse_number(syst_pacc_postcpb10))
```
```{r}
kruskal.test(x = RLdata$syst_cacc_postcpb10, g = RLdata$syst_pacc_postcpb10)
t.test(x = RLdata$syst_cacc_postcpb10, y = RLdata$syst_pacc_postcpb10)
```


##### 12: CA_MAP - PA_MAP

```{r}
RLdata <- 
  RLdata %>% 
  mutate(map_pacc_postcpb10 = parse_number(map_pacc_postcpb10))
```
```{r}
kruskal.test(x = RLdata$map_cacc_postcpb10, g = RLdata$map_pacc_postcpb10)
t.test(x = RLdata$map_cacc_postcpb10, y = RLdata$map_pacc_postcpb10)
```


### Radial Short:

#### Pre

##### 13: CA_Syst - PA_Syst

```{r}
kruskal.test(x = RSdata$syst_cacc_precpb, g = RSdata$syst_pacc_precpb)
t.test(x = RSdata$syst_cacc_precpb, y = RSdata$syst_pacc_precpb)
```

##### 14: CA_MAP - PA_MAP

```{r}
kruskal.test(x = RSdata$map_cacc_precpb, g = RSdata$map_pacc_precpb)
t.test(x = RSdata$map_cacc_precpb, y = RSdata$map_pacc_precpb)
```


#### Post 2 Minutes

##### 15: CA_Syst - PA_Syst

```{r}
kruskal.test(x = RSdata$syst_cacc_postcpb2, g = RSdata$syst_pacc_postcpb2)
t.test(x = RSdata$syst_cacc_postcpb2, y = RSdata$syst_pacc_postcpb2)
```

##### 16: CA_MAP - PA_MAP

```{r}
kruskal.test(x = RSdata$map_cacc_postcpb2, g = RSdata$map_pacc_postcpb2)
t.test(x = RSdata$map_cacc_postcpb2, y = RSdata$map_pacc_postcpb2)
```

#### Post 10 Minutes

##### 17: CA_Syst - PA_Syst

```{r}
kruskal.test(x = RSdata$syst_cacc_postcpb10, g = RSdata$syst_pacc_postcpb10)
t.test(x = RSdata$syst_cacc_postcpb10, y = RSdata$syst_pacc_postcpb10)
```

##### 18: CA_MAP - PA_MAP

```{r}
kruskal.test(x = RSdata$map_cacc_postcpb10, g = RSdata$map_pacc_postcpb10)
t.test(x = RSdata$map_cacc_postcpb10, y = RSdata$map_pacc_postcpb10)
```



### Comparisons:

#### Adding Proper Variables:

```{r}
BLdata <- 
  BLdata %>%
  mutate(CA_PA_systPreDiff = syst_cacc_precpb - syst_pacc_precpb,
         CA_PA_systPost2Diff =  syst_cacc_postcpb2 - syst_pacc_postcpb2,
         CA_PA_systPost10Diff = syst_cacc_postcpb10 - syst_pacc_postcpb10,
         CA_PA_mapPreDiff = map_cacc_precpb - map_pacc_precpb,
         CA_PA_mapPost2Diff =  map_cacc_postcpb2 - map_pacc_postcpb2,
         CA_PA_mapPost10Diff = map_cacc_postcpb10 - map_pacc_postcpb10
         )
```
```{r}
RLdata <- 
  RLdata %>%
  mutate(CA_PA_systPreDiff = syst_cacc_precpb - syst_pacc_precpb,
         CA_PA_systPost2Diff =  syst_cacc_postcpb2 - syst_pacc_postcpb2,
         CA_PA_systPost10Diff = syst_cacc_postcpb10 - syst_pacc_postcpb10,
         CA_PA_mapPreDiff = map_cacc_precpb - map_pacc_precpb,
         CA_PA_mapPost2Diff =  map_cacc_postcpb2 - map_pacc_postcpb2,
         CA_PA_mapPost10Diff = map_cacc_postcpb10 - map_pacc_postcpb10
         )
```
```{r}
RSdata <- 
  RSdata %>%
  mutate(CA_PA_systPreDiff = syst_cacc_precpb - syst_pacc_precpb,
         CA_PA_systPost2Diff =  syst_cacc_postcpb2 - syst_pacc_postcpb2,
         CA_PA_systPost10Diff = syst_cacc_postcpb10 - syst_pacc_postcpb10,
         CA_PA_mapPreDiff = map_cacc_precpb - map_pacc_precpb,
         CA_PA_mapPost2Diff =  map_cacc_postcpb2 - map_pacc_postcpb2,
         CA_PA_mapPost10Diff = map_cacc_postcpb10 - map_pacc_postcpb10
         )
```

#### Setting Up Data Pools:

```{r}
# BL and RL

BLdata$hyperlipid <-is.integer(BLdata$hyperlipid)
RLdata$hyperlipid <-is.integer(RLdata$hyperlipid)

BLdata$EF_pre <-is.double(BLdata$EF_pre)
RLdata$EF_pre <-is.double(RLdata$EF_pre)

BLdata$EF_post <-is.double(BLdata$EF_post)
RLdata$EF_post <-is.double(RLdata$EF_post)

BLdata$diast_pacc_precpb <-is.integer(BLdata$diast_pacc_precpb)
RLdata$diast_pacc_precp <-is.integer(RLdata$diast_pacc_precp)

BLdata$wave_pacc_postcpb10 <-is.integer(BLdata$wave_pacc_postcpb10)
RLdata$wave_pacc_postcpb10 <-is.integer(RLdata$wave_pacc_postcpb10)

BLdata$X.4 <- is.integer(BLdata$X.4)
RLdata$X.4 <- is.integer(RLdata$X.4)

BLRLdata <- bind_rows(BLdata, RLdata)
```


```{r}
# BL and RS

BLdata$syst_pacc_cicu <-is.integer(BLdata$syst_pacc_cicu)
RSdata$syst_pacc_cicu <-is.integer(RSdata$syst_pacc_cicu)

BLdata$diast_pacc_cicu <-is.integer(BLdata$diast_pacc_cicu)
RSdata$diast_pacc_cicu <-is.integer(RSdata$diast_pacc_cicu)

BLdata$map_pacc_cicu <-is.integer(BLdata$map_pacc_cicu)
RSdata$map_pacc_cicu <-is.integer(RSdata$map_pacc_cicu)

BLdata$wave_pacc_cicu <-is.integer(BLdata$wave_pacc_cicu)
RSdata$wave_pacc_cicu <-is.integer(RSdata$wave_pacc_cicu)

BLRSdata <- bind_rows(BLdata, RSdata)
```

```{r}
# RL and RS

RLdata$syst_pacc_cicu <- is.integer(RLdata$syst_pacc_cicu)
RSdata$syst_pacc_cicu <- is.integer(RSdata$syst_pacc_cicu)

RLdata$diast_pacc_cicu <- is.integer(RLdata$diast_pacc_cicu)
RSdata$diast_pacc_cicu <- is.integer(RSdata$diast_pacc_cicu)

RLdata$map_pacc_cicu <- is.integer(RLdata$map_pacc_cicu)
RSdata$map_pacc_cicu <- is.integer(RSdata$map_pacc_cicu)

RLdata$wave_pacc_cicu <- is.integer(RLdata$wave_pacc_cicu)
RSdata$wave_pacc_cicu <- is.integer(RSdata$wave_pacc_cicu)

RLRSdata <- bind_rows(RLdata, RSdata)
```





#### Pre

##### 1v7: BL(CA_Syst - PA_Syst) Vs. RL(CA_Syst - PA_Syst) 

```{r}
shapiro.test(x = is.numeric(BLRLdata$CA_PA_systPreDiff))

t.test(x = BLdata$CA_PA_systPreDiff, y = RLdata$CA_PA_systPreDiff)
```

##### 2v8: BL(CA_MAP - PA_MAP) Vs. RL(CA_MAP - PA_MAP) 

```{r}
kruskal.test(x = BLRLdata$CA_PA_mapPreDiff, g = BLRLdata$CA_PA_mapPreDiff)

t.test(x = BLdata$CA_PA_mapPreDiff, y = RLdata$CA_PA_mapPreDiff)
```

##### 1v13: BL(CA_Syst - PA_Syst) Vs. RS(CA_Syst - PA_Syst) 

```{r}
kruskal.test(x = BLRSdata$CA_PA_systPreDiff, g = BLRSdata$CA_PA_systPreDiff)

t.test(x = BLdata$CA_PA_systPreDiff, y = RSdata$CA_PA_systPreDiff)
```

##### 2v14: BL(CA_MAP - PA_MAP) Vs. RS(CA_MAP - PA_MAP)

```{r}
kruskal.test(x = BLRSdata$CA_PA_mapPreDiff, g = BLRSdata$CA_PA_mapPreDiff)
t.test(x = BLdata$CA_PA_mapPreDiff, y = RSdata$CA_PA_mapPreDiff)
```

##### 7v13: RL(CA_Syst - PA_Syst) Vs. RS(CA_Syst - PA_Syst) 

```{r}
kruskal.test(x = RLRSdata$CA_PA_systPreDiff, g = RLRSdata$CA_PA_systPreDiff)
t.test(x = RLdata$CA_PA_systPreDiff, y = RSdata$CA_PA_systPreDiff)
```

##### 8v14:RL(CA_MAP - PA_MAP) Vs. RS(CA_MAP - PA_MAP)

```{r}
kruskal.test(x = RLRSdata$CA_PA_mapPreDiff, g = RLRSdata$CA_PA_mapPreDiff)
t.test(x = RLdata$CA_PA_mapPreDiff, y = RSdata$CA_PA_mapPreDiff)
```


#### Post 2 Minutes

##### 3v9: BL(CA_Syst - PA_Syst) Vs. RL(CA_Syst - PA_Syst)

```{r}
kruskal.test(x = BLRLdata$CA_PA_systPost2Diff, g = BLRLdata$CA_PA_systPost2Diff)
t.test(x = BLdata$CA_PA_systPost2Diff, y = RLdata$CA_PA_systPost2Diff)
```

##### 4v10: BL(CA_MAP - PA_MAP) Vs. RL(CA_MAP - PA_MAP)

```{r}
kruskal.test()
t.test(x = BLdata$CA_PA_mapPost2Diff, y = RLdata$CA_PA_mapPost2Diff)
```

##### 3v15: BL(CA_Syst - PA_Syst) Vs. RS(CA_Syst - PA_Syst)

```{r}
kruskal.test(x = BLdata$CA_PA_systPost2Diff, g = RSdata$CA_PA_systPost2Diff)
t.test(x = BLdata$CA_PA_systPost2Diff, y = RSdata$CA_PA_systPost2Diff)
```

##### 4v16: BL(CA_MAP - PA_MAP) Vs. RS(CA_MAP - PA_MAP)

```{r}
kruskal.test(x = BLdata$CA_PA_mapPost2Diff, g = RSdata$CA_PA_mapPost2Diff)
t.test(x = BLdata$CA_PA_mapPost2Diff, y = RSdata$CA_PA_mapPost2Diff)
```

##### 9v15: RL(CA_Syst - PA_Syst) Vs. RS(CA_Syst - PA_Syst)

```{r}
t.test(x = RLdata$CA_PA_systPost2Diff, y = RSdata$CA_PA_systPost2Diff)
```

##### 10v16: RL(CA_MAP - PA_MAP) Vs. RS(CA_MAP - PA_MAP)

```{r}
t.test(x = RLdata$CA_PA_mapPost2Diff, y = RSdata$CA_PA_mapPost2Diff)
```

#### Post 10 Minutes

##### 5v11: BL(CA_Syst - PA_Syst) Vs. RL(CA_Syst - PA_Syst)

```{r}
t.test(x = BLdata$CA_PA_systPost10Diff, y = RLdata$CA_PA_systPost10Diff)
```

##### 6v12: BL(CA_MAP - PA_MAP) Vs. RL(CA_MAP - PA_MAP)

```{r}
t.test(x = BLdata$CA_PA_mapPost10Diff, y = RLdata$CA_PA_mapPost10Diff)
```

##### 5v17: BL(CA_Syst - PA_Syst) Vs. RS(CA_Syst - PA_Syst)

```{r}
kruskal.test(x = BLdata$CA_PA_systPost10Diff, g = RSdata$CA_PA_systPost10Diff)
t.test(x = BLdata$CA_PA_systPost10Diff, y = RSdata$CA_PA_systPost10Diff)
```

##### 6v18: BL(CA_MAP - PA_MAP) Vs. RS(CA_MAP - PA_MAP)

```{r}
kruskal.test(x = BLdata$CA_PA_mapPost10Diff, g = RSdata$CA_PA_mapPost10Diff)
t.test(x = BLdata$CA_PA_mapPost10Diff, y = RSdata$CA_PA_mapPost10Diff)
```

##### 11v17: RL(CA_Syst - PA_Syst) Vs. RS(CA_Syst - PA_Syst)

```{r}
t.test(x = RLdata$CA_PA_systPost10Diff, y = RSdata$CA_PA_systPost10Diff)
```

##### 12v18: RL(CA_MAP - PA_MAP) Vs. RS(CA_MAP - PA_MAP)

```{r}
t.test(x = RLdata$CA_PA_mapPost10Diff, y = RSdata$CA_PA_mapPost10Diff)
```

### Statistical Summary of Differences

#### Brachial Long

##### Pre


```{r}
BLdata %>%
  summarise(Mean_PreSyst = mean(CA_PA_systPreDiff),
            SD_PreSyst = sd(CA_PA_systPreDiff),
            Mean_PreMAP = mean(CA_PA_mapPreDiff),
            SD_PreMAP = sd(CA_PA_mapPreDiff)
            ) 
```

##### Post 2 Minutes

```{r}
BLdata %>%
  summarise(Mean_Post2Syst = mean(CA_PA_systPost2Diff),
            SD_Post2Syst = sd(CA_PA_systPost2Diff),
            Mean_Post2MAP = mean(CA_PA_mapPost2Diff),
            SD_Post2MAP = sd(CA_PA_mapPost2Diff)
            )
```

##### Post 10 Minutes

```{r}
BLdata %>%
  summarise(Mean_Post10Syst = mean(CA_PA_systPost10Diff),
            SD_Post10Syst = sd(CA_PA_systPost10Diff),
            Mean_Post10MAP = mean(CA_PA_mapPost10Diff),
            SD_Post10MAP = sd(CA_PA_mapPost10Diff)
            )
```

#### Radial Long

##### Pre


```{r}
RLdata %>%
  summarise(Mean_PreSyst = mean(CA_PA_systPreDiff),
            SD_PreSyst = sd(CA_PA_systPreDiff),
            Mean_PreMAP = mean(CA_PA_mapPreDiff),
            SD_PreMAP = sd(CA_PA_mapPreDiff)
            )
```

##### Post 2 Minutes

```{r}
RLdata %>%
  summarise(Mean_Post2Syst = mean(CA_PA_systPost2Diff),
            SD_Post2Syst = sd(CA_PA_systPost2Diff),
            Mean_Post2MAP = mean(CA_PA_mapPost2Diff),
            SD_Post2MAP = sd(CA_PA_mapPost2Diff)
            )
```

##### Post 10 Minutes

```{r}
RLdata %>%
  summarise(Mean_Post10Syst = mean(CA_PA_systPost10Diff,na.rm = TRUE),
            SD_Post10Syst = sd(CA_PA_systPost10Diff,na.rm = TRUE),
            Mean_Post10MAP = mean(CA_PA_mapPost10Diff,na.rm = TRUE),
            SD_Post10MAP = sd(CA_PA_mapPost10Diff,na.rm = TRUE)
            )
```

#### Radial Short

##### Pre


```{r}
RSdata %>%
  summarise(Mean_PreSyst = mean(CA_PA_systPreDiff),
            SD_PreSyst = sd(CA_PA_systPreDiff),
            Mean_PreMAP = mean(CA_PA_mapPreDiff),
            SD_PreMAP = sd(CA_PA_mapPreDiff)
            )
```

##### Post 2 Minutes

```{r}
RSdata %>%
  summarise(Mean_Post2Syst = mean(CA_PA_systPost2Diff),
            SD_Post2Syst = sd(CA_PA_systPost2Diff),
            Mean_Post2MAP = mean(CA_PA_mapPost2Diff),
            SD_Post2MAP = sd(CA_PA_mapPost2Diff)
            )
```

##### Post 10 Minutes

```{r}
RSdata %>%
  summarise(Mean_Post10Syst = mean(CA_PA_systPost10Diff),
            SD_Post10Syst = sd(CA_PA_systPost10Diff),
            Mean_Post10MAP = mean(CA_PA_mapPost10Diff),
            SD_Post10MAP = sd(CA_PA_mapPost10Diff)
            )
```











