---
title: "Linear Regression - Systolic"
author: "Matthew Maslow"
date: "2023-07-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

```{r message=FALSE, warning=FALSE}
library(tidyverse)
```
# Read in data
```{r}
Data <- read.csv("CSVdata.csv") 
Data <- Data %>% mutate(gender = ifelse(gender==1, 1, 0),
                        scCABG = ifelse(surgtype==1, 1, 0),
                        scAnyValve = ifelse(surgtype==2, 1, 0),
                        scCABGValve = ifelse(surgtype==3, 1, 0),
                        scOther = ifelse(surgtype==4, 1, 0),
                        bmiGE35 = ifelse(bmi>=35, 0, 1),
                        bmiGE40 = ifelse(bmi>=40, 0, 1),
                        hyperlipid = ifelse(hyperlipid=="0", 0, 1),
                        EF_pre = parse_number(EF_pre, na = "NA"),
                        EF_post = parse_number(EF_post, na = "NA")
                        )
```

# Adding Proper Variables:

```{r}
BLdata <- 
  Data %>% 
  filter(Group_char == "BL") %>%
  mutate(syst_pacc_postcpb10 = parse_number(syst_pacc_postcpb10),
    pctCA_PA_systPost2Diff = syst_cacc_postcpb2 - syst_pacc_postcpb2,
    pctCA_PA_systPost10Diff = syst_cacc_postcpb10-syst_pacc_postcpb10)
```

```{r}
RLdata <- 
  Data %>% 
  filter(Group_char == "RL") %>%
  mutate(syst_pacc_postcpb10 = parse_number(syst_pacc_postcpb10),
    pctCA_PA_systPost2Diff = syst_cacc_postcpb2 - syst_pacc_postcpb2,
    pctCA_PA_systPost10Diff = syst_cacc_postcpb10-syst_pacc_postcpb10)
```

```{r}
RSdata <- 
  Data %>% 
  filter(Group_char == "RS") %>%
  mutate(syst_pacc_postcpb10 = parse_number(syst_pacc_postcpb10),
    pctCA_PA_systPost2Diff = syst_cacc_postcpb2 - syst_pacc_postcpb2,
    pctCA_PA_systPost10Diff = syst_cacc_postcpb10-syst_pacc_postcpb10)
```


# Brachial Long (BL)

### Post 2 Minutes

#### Age

```{r}
age2BL <- lm(formula = pctCA_PA_systPost2Diff ~ age, data = BLdata)
summary(age2BL)
coef(age2BL)
confint(age2BL)
anova(age2BL)
cbind(age2BL, deparse.level = 2)
```


#### ASA PS

```{r}
asaps2BL <- lm(formula = pctCA_PA_systPost2Diff ~ asaps, data = BLdata)
summary(asaps2BL)
coef(asaps2BL)
confint(asaps2BL)
anova(asaps2BL)
cbind(asaps2BL, deparse.level = 2)
```

#### Male Vs. Female

```{r}
gender2BL <- lm(formula = pctCA_PA_systPost2Diff ~ gender, data = BLdata)
summary(gender2BL)
coef(gender2BL)
confint(gender2BL)
anova(gender2BL)
cbind(gender2BL, deparse.level = 2)
```

#### Weight

```{r}
wght2BL <- lm(formula = pctCA_PA_systPost2Diff ~ weight, data = BLdata)
summary(wght2BL)
coef(wght2BL)
confint(wght2BL)
anova(wght2BL)
cbind(wght2BL, deparse.level = 2)
```

#### Height

```{r}
hght2BL <- lm(formula = pctCA_PA_systPost2Diff ~ height, data = BLdata)
summary(hght2BL)
coef(hght2BL)
confint(hght2BL)
anova(hght2BL)
cbind(hght2BL, deparse.level = 2)
```

#### BMI (Continuous)

```{r}
bmi2BL <- lm(formula = pctCA_PA_systPost2Diff ~ bmi, data = BLdata)
summary(bmi2BL)
coef(bmi2BL)
confint(bmi2BL)
anova(bmi2BL)
cbind(bmi2BL, deparse.level = 2)
```

#### BMI ≥ 35 (binary: Yes=0, No=1)

```{r}
bmi35_2BL <- lm(formula = pctCA_PA_systPost2Diff ~ bmiGE35, data = BLdata)
summary(bmi35_2BL)
coef(bmi35_2BL)
confint(bmi35_2BL)
anova(bmi35_2BL)
cbind(bmi35_2BL, deparse.level = 2)
```

#### BMI ≥ 40 (binary: Yes=0, No=1)

```{r}
bmi40_2BL <- lm(formula = pctCA_PA_systPost2Diff ~ bmiGE40, data = BLdata)
summary(bmi40_2BL)
coef(bmi40_2BL)
confint(bmi40_2BL)
anova(bmi40_2BL)
cbind(bmi40_2BL, deparse.level = 2)
```

#### -------------------------------------------

#### AF

```{r}
af2BL <- lm(formula = pctCA_PA_systPost2Diff ~ af, data = BLdata, family = "binomial")
summary(af2BL)
coef(af2BL)
confint(af2BL)
anova(af2BL)
cbind(af2BL,deparse.level = 2)
```

#### DM

```{r}
dm2BL <- lm(formula = pctCA_PA_systPost2Diff ~ dm, data = BLdata, family = "binomial")
summary(dm2BL)
coef(dm2BL)
confint(dm2BL)
anova(dm2BL)
cbind(dm2BL, deparse.level = 2)
```

#### CKD

```{r}
ckd2BL <- lm(formula = pctCA_PA_systPost2Diff ~ ckd, data = BLdata, family = "binomial")
summary(ckd2BL)
coef(ckd2BL)
confint(ckd2BL)
anova(ckd2BL)
cbind(ckd2BL, deparse.level = 2)
```

#### HTN

```{r}
htn2BL <- lm(formula = pctCA_PA_systPost2Diff ~ htn, data = BLdata)
summary(htn2BL)
coef(htn2BL)
confint(htn2BL)
anova(htn2BL)
cbind(htn2BL, deparse.level = 2)
```

#### COPD

```{r}
copd2BL <- lm(formula = pctCA_PA_systPost2Diff ~ copd, data = BLdata, family = "binomial")
summary(copd2BL)
coef(copd2BL)
confint(copd2BL)
anova(copd2BL)
cbind(copd2BL, deparse.level = 2)
```

#### Hyperlipidemia

```{r}
hyper2BL <- lm(formula = pctCA_PA_systPost2Diff ~ hyperlipid, data = BLdata, family = "binomial")
summary(hyper2BL)
coef(hyper2BL)
confint(hyper2BL)
anova(hyper2BL)
cbind(hyper2BL, deparse.level = 2)
```

#### OSA

```{r}
osa2BL <- lm(formula = pctCA_PA_systPost2Diff ~ osa, data = BLdata)
summary(osa2BL)
coef(osa2BL)
confint(osa2BL)
anova(osa2BL)
cbind(osa2BL, deparse.level = 2)
```

#### PAD

```{r}
pad2BL <- lm(formula = pctCA_PA_systPost2Diff ~ pad, data = BLdata)
summary(pad2BL)
coef(pad2BL)
confint(pad2BL)
anova(pad2BL)
cbind(pad2BL, deparse.level = 2)
```

#### Total (# comorbidities) 

```{r}
tnComorbid2BL <- lm(formula = pctCA_PA_systPost2Diff ~ totnum_comorbid, data = BLdata)
summary(tnComorbid2BL)
coef(tnComorbid2BL)
confint(tnComorbid2BL)
anova(tnComorbid2BL)
cbind(tnComorbid2BL, deparse.level = 2)
```

#### -------------------------------------------

#### Surgical Code (CABG=1, Any Valves =2, CABG+valve=3, Other=4)

##### CABG = 1

```{r}
sc1_2BL <- lm(formula = pctCA_PA_systPost2Diff ~ scCABG, data = BLdata)
summary(sc1_2BL)
coef(sc1_2BL)
confint(sc1_2BL)
anova(sc1_2BL)
cbind(sc1_2BL, deparse.level = 2)
```

##### Any Valve = 2

```{r}
sc2_2BL <- lm(formula = pctCA_PA_systPost2Diff ~ scAnyValve, data = BLdata)
summary(sc2_2BL)
coef(sc2_2BL)
confint(sc2_2BL)
anova(sc2_2BL)
cbind(sc2_2BL, deparse.level = 2)
```

##### CABG + Valve = 3

```{r}
sc3_2BL <- lm(formula = pctCA_PA_systPost2Diff ~ scCABGValve, data = BLdata)
summary(sc3_2BL)
coef(sc3_2BL)
confint(sc3_2BL)
anova(sc3_2BL)
cbind(sc3_2BL, deparse.level = 2)
```

##### Other = 4

```{r}
sc4_2BL <- lm(formula = pctCA_PA_systPost2Diff ~ scOther, data = BLdata)
summary(sc4_2BL)
coef(sc4_2BL)
confint(sc4_2BL)
anova(sc4_2BL)
cbind(sc4_2BL, deparse.level = 2)
```

#### -------------------------------------------

#### Crystalloid Use

```{r}
CrystUse2BL <- lm(formula = pctCA_PA_systPost2Diff ~ crystalloid, data = BLdata)
summary(CrystUse2BL)
coef(CrystUse2BL)
confint(CrystUse2BL)
anova(CrystUse2BL)
cbind(CrystUse2BL, deparse.level = 2)
```

#### PRBC

```{r}
prbc2BL <- lm(formula = pctCA_PA_systPost2Diff ~ prbc, data = BLdata)
summary(prbc2BL)
coef(prbc2BL)
confint(prbc2BL)
anova(prbc2BL)
cbind(prbc2BL, deparse.level = 2)
```

#### Autologous

```{r}
autolgs2BL <- lm(formula = pctCA_PA_systPost2Diff ~ autologous, data = BLdata)
summary(autolgs2BL)
coef(autolgs2BL)
confint(autolgs2BL)
anova(autolgs2BL)
cbind(autolgs2BL, deparse.level = 2)
```

#### Total # Colloid Products 

```{r}
tnColloid2BL <- lm(formula = pctCA_PA_systPost2Diff ~ totnum_colloid, data = BLdata)
summary(tnColloid2BL)
coef(tnColloid2BL)
confint(tnColloid2BL)
anova(tnColloid2BL)
cbind(tnColloid2BL, deparse.level = 2)
```

#### Total Colloiod prducts (mls) 

```{r}
tmlsColloid2BL <- lm(formula = pctCA_PA_systPost2Diff ~ totml_colloid, data = BLdata)
summary(tmlsColloid2BL)
coef(tmlsColloid2BL)
confint(tmlsColloid2BL)
anova(tmlsColloid2BL)
cbind(tmlsColloid2BL, deparse.level = 2)
```

#### Cell Saver volume retained

```{r}
csvol2BL <- lm(formula = pctCA_PA_systPost2Diff ~ cellsaver_vol, data = BLdata)
summary(csvol2BL)
coef(csvol2BL)
confint(csvol2BL)
anova(csvol2BL)
cbind(csvol2BL, deparse.level = 2)
```

#### Urine Output

```{r}
urine2BL <- lm(formula = pctCA_PA_systPost2Diff ~ urine, data = BLdata)
summary(urine2BL)
coef(urine2BL)
confint(urine2BL)
anova(urine2BL)
cbind(urine2BL, deparse.level = 2)
```


#### -------------------------------------------

#### CPB duration (min)

```{r}
cpbDur2BL <- lm(formula = pctCA_PA_systPost2Diff ~ cpb_duration, data = BLdata)
summary(cpbDur2BL)
coef(cpbDur2BL)
confint(cpbDur2BL)
anova(cpbDur2BL)
cbind(cpbDur2BL, deparse.level = 2)
```

#### Aortic Clamp time (min)

```{r}
acTime2BL <- lm(formula = pctCA_PA_systPost2Diff ~ aortic_clamp_time, data = BLdata)
summary(acTime2BL)
coef(acTime2BL)
confint(acTime2BL)
anova(acTime2BL)
cbind(acTime2BL, deparse.level = 2)
```

#### Ejection Fraction PRE (%)

```{r}
efPre2BL <- lm(formula = pctCA_PA_systPost2Diff ~ EF_pre, data = BLdata)
summary(efPre2BL)
coef(efPre2BL)
confint(efPre2BL)
anova(efPre2BL)
cbind(efPre2BL, deparse.level = 2)
```

#### Ejection Fraction POST (%)

```{r}
efPost2BL <- lm(formula = pctCA_PA_systPost2Diff ~ EF_post, data = BLdata)
summary(efPost2BL)
coef(efPost2BL)
confint(efPost2BL)
anova(efPost2BL)
cbind(efPost2BL, deparse.level = 2)
```


### Post 10 Minutes

#### Age

```{r}
age10BL <- lm(formula = pctCA_PA_systPost10Diff ~ age, data = BLdata)
summary(age10BL)
coef(age10BL)
confint(age10BL)
anova(age10BL)
cbind(age10BL, deparse.level = 2)
```

#### ASA PS

```{r}
asaps10BL <- lm(formula = pctCA_PA_systPost10Diff ~ asaps, data = BLdata)
summary(asaps10BL)
coef(asaps10BL)
confint(asaps10BL)
anova(asaps10BL)
cbind(asaps10BL, deparse.level = 2)
```

#### Male Vs. Female

```{r}
gender10BL <- lm(formula = pctCA_PA_systPost10Diff ~ gender, data = BLdata)
summary(gender10BL)
coef(gender10BL)
confint(gender10BL)
anova(gender10BL)
cbind(gender10BL, deparse.level = 2)
```

#### Weight

```{r}
wght10BL <- lm(formula = pctCA_PA_systPost10Diff ~ weight, data = BLdata)
summary(wght10BL)
coef(wght10BL)
confint(wght10BL)
anova(wght10BL)
cbind(wght10BL, deparse.level = 2)
```

#### Height

```{r}
hght10BL <- lm(formula = pctCA_PA_systPost10Diff ~ height, data = BLdata)
summary(hght10BL)
coef(hght10BL)
confint(hght10BL)
anova(hght10BL)
cbind(hght10BL, deparse.level = 2)
```

#### BMI (Continuous)

```{r}
bmi10BL <- lm(formula = pctCA_PA_systPost10Diff ~ bmi, data = BLdata)
summary(bmi10BL)
coef(bmi10BL)
confint(bmi10BL)
anova(bmi10BL)
cbind(bmi10BL, deparse.level = 2)
```

#### BMI ≥ 35 (binary: Yes=1, No=2)

```{r}
bmi35_10BL <- lm(formula = pctCA_PA_systPost10Diff ~ bmiGE35, data = BLdata)
summary(bmi35_10BL)
coef(bmi35_10BL)
confint(bmi35_10BL)
anova(bmi35_10BL)
cbind(bmi35_10BL, deparse.level = 2)
```

#### BMI ≥ 40 (binary: Yes=1, No=2)

```{r}
bmi40_10BL <- lm(formula = pctCA_PA_systPost10Diff ~ bmiGE40, data = BLdata)
summary(bmi40_10BL)
coef(bmi40_10BL)
confint(bmi40_10BL)
anova(bmi40_10BL)
cbind(bmi40_10BL, deparse.level = 2)
```

#### -------------------------------------------

#### AF

```{r}
af10BL <- lm(formula = pctCA_PA_systPost10Diff ~ af, data = BLdata)
summary(af10BL)
coef(af10BL)
confint(af10BL)
anova(af10BL)
cbind(af10BL, deparse.level = 2)
```

#### DM

```{r}
dm10BL <- lm(formula = pctCA_PA_systPost10Diff ~ dm, data = BLdata)
summary(dm10BL)
coef(dm10BL)
confint(dm10BL)
anova(dm10BL)
cbind(dm10BL, deparse.level = 2)
```

#### CKD

```{r}
ckd10BL <- lm(formula = pctCA_PA_systPost10Diff ~ ckd, data = BLdata)
summary(ckd10BL)
coef(ckd10BL)
confint(ckd10BL)
anova(ckd10BL)
cbind(ckd10BL, deparse.level = 2)
```

#### HTN

```{r}
htn10BL <- lm(formula = pctCA_PA_systPost10Diff ~ htn, data = BLdata)
summary(htn10BL)
coef(htn10BL)
confint(htn10BL)
anova(htn10BL)
cbind(htn10BL, deparse.level = 2)
```

#### COPD

```{r}
copd10BL <- lm(formula = pctCA_PA_systPost10Diff ~ copd, data = BLdata)
summary(copd10BL)
coef(copd10BL)
confint(copd10BL)
anova(copd10BL)
cbind(copd10BL, deparse.level = 2)
```

#### Hyperlipidemia

```{r}
hyper10BL <- lm(formula = pctCA_PA_systPost10Diff ~ hyperlipid, data = BLdata)
summary(hyper10BL)
coef(hyper10BL)
confint(hyper10BL)
anova(hyper10BL)
cbind(hyper10BL, deparse.level = 2)
```

#### OSA

```{r}
osa10BL <- lm(formula = pctCA_PA_systPost10Diff ~ osa, data = BLdata)
summary(osa10BL)
coef(osa10BL)
confint(osa10BL)
anova(osa10BL)
cbind(osa10BL, deparse.level = 2)
```

#### PAD

```{r}
pad10BL <- lm(formula = pctCA_PA_systPost10Diff ~ pad, data = BLdata)
summary(pad10BL)
coef(pad10BL)
confint(pad10BL)
anova(pad10BL)
cbind(pad10BL, deparse.level = 2)
```

#### Total (# comorbidities) 

```{r}
tnComorbid10BL <- lm(formula = pctCA_PA_systPost10Diff ~ totnum_comorbid, data = BLdata)
summary(tnComorbid10BL)
coef(tnComorbid10BL)
confint(tnComorbid10BL)
anova(tnComorbid10BL)
cbind(tnComorbid10BL, deparse.level = 2)
```

#### -------------------------------------------

#### Surgical Code (CABG=1, Any Valves =2, CABG+valve=3, Other=4) 

##### CABG = 1

```{r}
sc1_10BL <- lm(formula = pctCA_PA_systPost10Diff ~ scCABG, data = BLdata)
summary(sc1_10BL)
coef(sc1_10BL)
confint(sc1_10BL)
anova(sc1_10BL)
cbind(sc1_10BL, deparse.level = 2)
```

##### Any Valve = 2

```{r}
sc2_10BL <- lm(formula = pctCA_PA_systPost10Diff ~ scAnyValve, data = BLdata)
summary(sc2_10BL)
coef(sc2_10BL)
confint(sc2_10BL)
anova(sc2_10BL)
cbind(sc2_10BL, deparse.level = 2)
```

##### CABG + Valve = 3

```{r}
sc3_10BL <- lm(formula = pctCA_PA_systPost10Diff ~ scCABGValve, data = BLdata)
summary(sc3_10BL)
coef(sc3_10BL)
confint(sc3_10BL)
anova(sc3_10BL)
cbind(sc3_10BL, deparse.level = 2)
```

##### Other = 4

```{r}
sc4_10BL <- lm(formula = pctCA_PA_systPost10Diff ~ scOther, data = BLdata)
summary(sc4_10BL)
coef(sc4_10BL)
confint(sc4_10BL)
anova(sc4_10BL)
cbind(sc4_10BL, deparse.level = 2)
```

#### -------------------------------------------

#### Crystalloid Use

```{r}
CrystUse10BL <- lm(formula = pctCA_PA_systPost10Diff ~ crystalloid, data = BLdata)
summary(CrystUse10BL)
coef(CrystUse10BL)
confint(CrystUse10BL)
anova(CrystUse10BL)
cbind(CrystUse10BL, deparse.level = 2)
```

#### PRBC

```{r}
prbc10BL <- lm(formula = pctCA_PA_systPost10Diff ~ prbc, data = BLdata)
summary(prbc10BL)
coef(prbc10BL)
confint(prbc10BL)
anova(prbc10BL)
cbind(prbc10BL, deparse.level = 2)
```

#### Autologous

```{r}
autolgs10BL <- lm(formula = pctCA_PA_systPost10Diff ~ autologous, data = BLdata)
summary(autolgs10BL)
coef(autolgs10BL)
confint(autolgs10BL)
anova(autolgs10BL)
cbind(autolgs10BL, deparse.level = 2)
```

#### Total # Colloid Products 

```{r}
tnColloid10BL <- lm(formula = pctCA_PA_systPost10Diff ~ totnum_colloid, data = BLdata)
summary(tnColloid10BL)
coef(tnColloid10BL)
confint(autolgs10BL)
anova(tnColloid10BL)
cbind(tnColloid10BL, deparse.level = 2)
```

#### Total Colloiod prducts (mls) 

```{r}
tmlsColloid10BL <- lm(formula = pctCA_PA_systPost10Diff ~ totml_colloid, data = BLdata)
summary(tmlsColloid10BL)
coef(tmlsColloid10BL)
confint(tmlsColloid10BL)
anova(tmlsColloid10BL)
cbind(tmlsColloid10BL, deparse.level = 2)
```

#### Cell Saver volume retained

```{r}
csvol10BL <- lm(formula = pctCA_PA_systPost10Diff ~ cellsaver_vol, data = BLdata)
summary(csvol10BL)
coef(csvol10BL)
confint(csvol10BL)
anova(csvol10BL)
cbind(csvol10BL, deparse.level = 2)
```

#### Urine Output

```{r}
urine10BL <- lm(formula = pctCA_PA_systPost10Diff ~ urine, data = BLdata)
summary(urine10BL)
coef(urine10BL)
confint(urine10BL)
anova(urine10BL)
cbind(urine10BL, deparse.level = 2)
```


#### -------------------------------------------

#### CPB duration (min)

```{r}
cpbDur10BL <- lm(formula = pctCA_PA_systPost10Diff ~ cpb_duration, data = BLdata)
summary(cpbDur10BL)
coef(cpbDur10BL)
confint(cpbDur10BL)
anova(cpbDur10BL)
cbind(cpbDur10BL, deparse.level = 2)
```

#### Aortic Clamp time (min)

```{r}
acTime10BL <- lm(formula = pctCA_PA_systPost10Diff ~ aortic_clamp_time, data = BLdata)
summary(acTime10BL)
coef(acTime10BL)
confint(acTime10BL)
anova(acTime10BL)
cbind(acTime10BL, deparse.level = 2)
```

#### Ejection Fraction PRE (%)

```{r}
efPre10BL <- lm(formula = pctCA_PA_systPost10Diff ~ EF_pre, data = BLdata)
summary(efPre10BL)
coef(efPre10BL)
confint(efPre10BL)
anova(efPre10BL)
cbind(efPre10BL, deparse.level = 2)
```

#### Ejection Fraction POST (%)

```{r}
efPost10BL <- lm(formula = pctCA_PA_systPost10Diff ~ EF_post, data = BLdata)
summary(efPost10BL)
coef(efPost10BL)
confint(efPost10BL)
anova(efPost10BL)
cbind(efPost10BL, deparse.level = 2)
```



# Radial Long (RL)

### Post 2 Minutes

#### Age

```{r}
age2RL <- lm(formula = pctCA_PA_systPost2Diff ~ age, data = RLdata)
summary(age2RL)
coef(age2RL)
confint(age2RL)
anova(age2RL)
cbind(age2RL, deparse.level = 2)
```


#### ASA PS

```{r}
asaps2RL <- lm(formula = pctCA_PA_systPost2Diff ~ asaps, data = RLdata)
summary(asaps2RL)
coef(asaps2RL)
confint(asaps2RL)
anova(asaps2RL)
cbind(asaps2RL, deparse.level = 2)
```

#### Male Vs. Female

```{r}
gender2RL <- lm(formula = pctCA_PA_systPost2Diff ~ gender, data = RLdata)
summary(gender2RL)
coef(gender2RL)
confint(gender2RL)
anova(gender2RL)
cbind(gender2RL, deparse.level = 2)
```

#### Weight

```{r}
wght2RL <- lm(formula = pctCA_PA_systPost2Diff ~ weight, data = RLdata)
summary(wght2RL)
coef(wght2RL)
confint(wght2RL)
anova(wght2RL)
cbind(wght2RL, deparse.level = 2)
```

#### Height

```{r}
hght2RL <- lm(formula = pctCA_PA_systPost2Diff ~ height, data = RLdata)
summary(hght2RL)
coef(hght2RL)
confint(hght2RL)
anova(hght2RL)
cbind(hght2RL, deparse.level = 2)
```

#### BMI (Continuous)

```{r}
bmi2RL <- lm(formula = pctCA_PA_systPost2Diff ~ bmi, data = RLdata)
summary(bmi2RL)
coef(bmi2RL)
confint(bmi2RL)
anova(bmi2RL)
cbind(bmi2RL, deparse.level = 2)
```

#### BMI ≥ 35 (binary: Yes=1, No=2)

```{r}
bmi35_2RL <- lm(formula = pctCA_PA_systPost2Diff ~ bmiGE35, data = RLdata)
summary(bmi35_2RL)
coef(bmi35_2RL)
confint(bmi35_2RL)
anova(bmi35_2RL)
cbind(bmi35_2RL, deparse.level = 2)
```

#### BMI ≥ 40 (binary: Yes=1, No=2)

```{r}
bmi40_2RL <- lm(formula = pctCA_PA_systPost2Diff ~ bmiGE40, data = RLdata)
summary(bmi40_2RL)
coef(bmi40_2RL)
confint(bmi40_2RL)
anova(bmi40_2RL)
cbind(bmi40_2RL, deparse.level = 2)
```

#### -------------------------------------------

#### AF

```{r}
af2RL <- lm(formula = pctCA_PA_systPost2Diff ~ af, data = RLdata, family = "binomial")
summary(af2RL)
coef(af2RL)
confint(af2RL)
anova(af2RL)
cbind(af2RL,deparse.level = 2)
```

#### DM

```{r}
dm2RL <- lm(formula = pctCA_PA_systPost2Diff ~ dm, data = RLdata, family = "binomial")
summary(dm2RL)
coef(dm2RL)
confint(dm2RL)
anova(dm2RL)
cbind(dm2RL, deparse.level = 2)
```

#### CKD

```{r}
ckd2RL <- lm(formula = pctCA_PA_systPost2Diff ~ ckd, data = RLdata, family = "binomial")
summary(ckd2RL)
coef(ckd2RL)
confint(ckd2RL)
anova(ckd2RL)
cbind(ckd2RL, deparse.level = 2)
```

#### HTN

```{r}
htn2RL <- lm(formula = pctCA_PA_systPost2Diff ~ htn, data = RLdata)
summary(htn2RL)
coef(htn2RL)
confint(htn2RL)
anova(htn2RL)
cbind(htn2RL, deparse.level = 2)
```

#### COPD

```{r}
copd2RL <- lm(formula = pctCA_PA_systPost2Diff ~ copd, data = RLdata, family = "binomial")
summary(copd2RL)
coef(copd2RL)
confint(copd2RL)
anova(copd2RL)
cbind(copd2RL, deparse.level = 2)
```

#### Hyperlipidemia

```{r}
hyper2RL <- lm(formula = pctCA_PA_systPost2Diff ~ hyperlipid, data = RLdata, family = "binomial")
summary(hyper2RL)
coef(hyper2RL)
confint(hyper2RL)
anova(hyper2RL)
cbind(hyper2RL, deparse.level = 2)
```

#### OSA

```{r}
osa2RL <- lm(formula = pctCA_PA_systPost2Diff ~ osa, data = RLdata)
summary(osa2RL)
coef(osa2RL)
confint(osa2RL)
anova(osa2RL)
cbind(osa2RL, deparse.level = 2)
```

#### PAD

```{r}
pad2RL <- lm(formula = pctCA_PA_systPost2Diff ~ pad, data = RLdata)
summary(pad2RL)
coef(pad2RL)
confint(pad2RL)
anova(pad2RL)
cbind(pad2RL, deparse.level = 2)
```

#### Total (# comorbidities) 

```{r}
tnComorbid2RL <- lm(formula = pctCA_PA_systPost2Diff ~ totnum_comorbid, data = RLdata)
summary(tnComorbid2RL)
coef(tnComorbid2RL)
confint(tnComorbid2RL)
anova(tnComorbid2RL)
cbind(tnComorbid2RL, deparse.level = 2)
```

#### -------------------------------------------

#### Surgical Code (CABG=1, Any Valves =2, CABG+valve=3, Other=4) 

##### CABG = 1

```{r}
sc1_2RL <- lm(formula = pctCA_PA_systPost2Diff ~ scCABG, data = RLdata)
summary(sc1_2RL)
coef(sc1_2RL)
confint(sc1_2RL)
anova(sc1_2RL)
cbind(sc1_2RL, deparse.level = 2)
```

##### Any Valve = 2

```{r}
sc2_2RL <- lm(formula = pctCA_PA_systPost2Diff ~ scAnyValve, data = RLdata)
summary(sc2_2RL)
coef(sc2_2RL)
confint(sc2_2RL)
anova(sc2_2RL)
cbind(sc2_2RL, deparse.level = 2)
```

##### CABG + Valve = 3

```{r}
sc3_2RL <- lm(formula = pctCA_PA_systPost2Diff ~ scCABGValve, data = RLdata)
summary(sc3_2RL)
coef(sc3_2RL)
confint(sc3_2RL)
anova(sc3_2RL)
cbind(sc3_2RL, deparse.level = 2)
```

##### Other = 4

```{r}
sc4_2RL <- lm(formula = pctCA_PA_systPost2Diff ~ scOther, data = RLdata)
summary(sc4_2RL)
coef(sc4_2RL)
confint(sc4_2RL)
anova(sc4_2RL)
cbind(sc4_2RL, deparse.level = 2)
```

#### -------------------------------------------

#### Crystalloid Use

```{r}
CrystUse2RL <- lm(formula = pctCA_PA_systPost2Diff ~ crystalloid, data = RLdata)
summary(CrystUse2RL)
coef(CrystUse2RL)
confint(CrystUse2RL)
anova(CrystUse2RL)
cbind(CrystUse2RL, deparse.level = 2)
```

#### PRBC

```{r}
prbc2RL <- lm(formula = pctCA_PA_systPost2Diff ~ prbc, data = RLdata)
summary(prbc2RL)
coef(prbc2RL)
confint(prbc2RL)
anova(prbc2RL)
cbind(prbc2RL, deparse.level = 2)
```

#### Autologous

```{r}
autolgs2RL <- lm(formula = pctCA_PA_systPost2Diff ~ autologous, data = RLdata)
summary(autolgs2RL)
coef(autolgs2RL)
confint(autolgs2RL)
anova(autolgs2RL)
cbind(autolgs2RL, deparse.level = 2)
```

#### Total # Colloid Products 

```{r}
tnColloid2RL <- lm(formula = pctCA_PA_systPost2Diff ~ totnum_colloid, data = RLdata)
summary(tnColloid2RL)
coef(tnColloid2RL)
confint(tnColloid2RL)
anova(tnColloid2RL)
cbind(tnColloid2RL, deparse.level = 2)
```

#### Total Colloiod prducts (mls) 

```{r}
tmlsColloid2RL <- lm(formula = pctCA_PA_systPost2Diff ~ totml_colloid, data = RLdata)
summary(tmlsColloid2RL)
coef(tmlsColloid2RL)
confint(tmlsColloid2RL)
anova(tmlsColloid2RL)
cbind(tmlsColloid2RL, deparse.level = 2)
```

#### Cell Saver volume retained

```{r}
csvol2RL <- lm(formula = pctCA_PA_systPost2Diff ~ cellsaver_vol, data = RLdata)
summary(csvol2RL)
coef(csvol2RL)
confint(csvol2RL)
anova(csvol2RL)
cbind(csvol2RL, deparse.level = 2)
```

#### Urine Output

```{r}
urine2RL <- lm(formula = pctCA_PA_systPost2Diff ~ urine, data = RLdata)
summary(urine2RL)
coef(urine2RL)
confint(urine2RL)
anova(urine2RL)
cbind(urine2RL, deparse.level = 2)
```


#### -------------------------------------------

#### CPB duration (min)

```{r}
cpbDur2RL <- lm(formula = pctCA_PA_systPost2Diff ~ cpb_duration, data = RLdata)
summary(cpbDur2RL)
coef(cpbDur2RL)
confint(cpbDur2RL)
anova(cpbDur2RL)
cbind(cpbDur2RL, deparse.level = 2)
```

#### Aortic Clamp time (min)

```{r}
acTime2RL <- lm(formula = pctCA_PA_systPost2Diff ~ aortic_clamp_time, data = RLdata)
summary(acTime2RL)
coef(acTime2RL)
confint(acTime2RL)
anova(acTime2RL)
cbind(acTime2RL, deparse.level = 2)
```

#### Ejection Fraction PRE (%)

```{r}
efPre2RL <- lm(formula = pctCA_PA_systPost2Diff ~ EF_pre, data = RLdata)
summary(efPre2RL)
coef(efPre2RL)
confint(efPre2RL)
anova(efPre2RL)
cbind(efPre2RL, deparse.level = 2)
```

#### Ejection Fraction POST (%)

```{r}
efPost2RL <- lm(formula = pctCA_PA_systPost2Diff ~ EF_post, data = RLdata)
summary(efPost2RL)
coef(efPost2RL)
confint(efPost2RL)
anova(efPost2RL)
cbind(efPost2RL, deparse.level = 2)
```


### Post 10 Minutes

#### Age

```{r}
age10RL <- lm(formula = pctCA_PA_systPost10Diff ~ age, data = RLdata)
summary(age10RL)
coef(age10RL)
confint(age10RL)
anova(age10RL)
cbind(age10RL, deparse.level = 2)
```

#### ASA PS

```{r}
asaps10RL <- lm(formula = pctCA_PA_systPost10Diff ~ asaps, data = RLdata)
summary(asaps10RL)
coef(asaps10RL)
confint(asaps10RL)
anova(asaps10RL)
cbind(asaps10RL, deparse.level = 2)
```

#### Male Vs. Female

```{r}
gender10RL <- lm(formula = pctCA_PA_systPost10Diff ~ gender, data = RLdata)
summary(gender10RL)
coef(gender10RL)
confint(gender10RL)
anova(gender10RL)
cbind(gender10RL, deparse.level = 2)
```

#### Weight

```{r}
wght10RL <- lm(formula = pctCA_PA_systPost10Diff ~ weight, data = RLdata)
summary(wght10RL)
coef(wght10RL)
confint(wght10RL)
anova(wght10RL)
cbind(wght10RL, deparse.level = 2)
```

#### Height

```{r}
hght10RL <- lm(formula = pctCA_PA_systPost10Diff ~ height, data = RLdata)
summary(hght10RL)
coef(hght10RL)
confint(hght10RL)
anova(hght10RL)
cbind(hght10RL, deparse.level = 2)
```

#### BMI (Continuous)

```{r}
bmi10RL <- lm(formula = pctCA_PA_systPost10Diff ~ bmi, data = RLdata)
summary(bmi10RL)
coef(bmi10RL)
confint(bmi10RL)
anova(bmi10RL)
cbind(bmi10RL, deparse.level = 2)
```

#### BMI ≥ 35 (binary: Yes=1, No=2)

```{r}
bmi35_10RL <- lm(formula = pctCA_PA_systPost10Diff ~ bmiGE35, data = RLdata)
summary(bmi35_10RL)
coef(bmi35_10RL)
confint(bmi35_10RL)
anova(bmi35_10RL)
cbind(bmi35_10RL, deparse.level = 2)
```

#### BMI ≥ 40 (binary: Yes=1, No=2)

```{r}
bmi40_10RL <- lm(formula = pctCA_PA_systPost10Diff ~ bmiGE40, data = RLdata)
summary(bmi40_10RL)
coef(bmi40_10RL)
confint(bmi40_10RL)
anova(bmi40_10RL)
cbind(bmi40_10RL, deparse.level = 2)
```

#### -------------------------------------------

#### AF

```{r}
af10RL <- lm(formula = pctCA_PA_systPost10Diff ~ af, data = RLdata)
summary(af10RL)
coef(af10RL)
confint(af10RL)
anova(af10RL)
cbind(af10RL, deparse.level = 2)
```

#### DM

```{r}
dm10RL <- lm(formula = pctCA_PA_systPost10Diff ~ dm, data = RLdata)
summary(dm10RL)
coef(dm10RL)
confint(dm10RL)
anova(dm10RL)
cbind(dm10RL, deparse.level = 2)
```

#### CKD

```{r}
ckd10RL <- lm(formula = pctCA_PA_systPost10Diff ~ ckd, data = RLdata)
summary(ckd10RL)
coef(ckd10RL)
confint(ckd10RL)
anova(ckd10RL)
cbind(ckd10RL, deparse.level = 2)
```

#### HTN

```{r}
htn10RL <- lm(formula = pctCA_PA_systPost10Diff ~ htn, data = RLdata)
summary(htn10RL)
coef(htn10RL)
confint(htn10RL)
anova(htn10RL)
cbind(htn10RL, deparse.level = 2)
```

#### COPD

```{r}
copd10RL <- lm(formula = pctCA_PA_systPost10Diff ~ copd, data = RLdata)
summary(copd10RL)
coef(copd10RL)
confint(copd10RL)
anova(copd10RL)
cbind(copd10RL, deparse.level = 2)
```

#### Hyperlipidemia

```{r}
hyper10RL <- lm(formula = pctCA_PA_systPost10Diff ~ hyperlipid, data = RLdata)
summary(hyper10RL)
coef(hyper10RL)
confint(hyper10RL)
anova(hyper10RL)
cbind(hyper10RL, deparse.level = 2)
```

#### OSA

```{r}
osa10RL <- lm(formula = pctCA_PA_systPost10Diff ~ osa, data = RLdata)
summary(osa10RL)
coef(osa10RL)
confint(osa10RL)
anova(osa10RL)
cbind(osa10RL, deparse.level = 2)
```

#### PAD

```{r}
pad10RL <- lm(formula = pctCA_PA_systPost10Diff ~ pad, data = RLdata)
summary(pad10RL)
coef(pad10RL)
confint(pad10RL)
anova(pad10RL)
cbind(pad10RL, deparse.level = 2)
```

#### Total (# comorbidities) 

```{r}
tnComorbid10RL <- lm(formula = pctCA_PA_systPost10Diff ~ totnum_comorbid, data = RLdata)
summary(tnComorbid10RL)
coef(tnComorbid10RL)
confint(tnComorbid10RL)
anova(tnComorbid10RL)
cbind(tnComorbid10RL, deparse.level = 2)
```

#### -------------------------------------------

#### Surgical Code (CABG=1, Any Valves =2, CABG+valve=3, Other=4) 

##### CABG = 1

```{r}
sc1_10RL <- lm(formula = pctCA_PA_systPost10Diff ~ scCABG, data = RLdata)
summary(sc1_10RL)
coef(sc1_10RL)
confint(sc1_10RL)
anova(sc1_10RL)
cbind(sc1_10RL, deparse.level = 2)
```

##### Any Valve = 2

```{r}
sc2_10RL <- lm(formula = pctCA_PA_systPost10Diff ~ scAnyValve, data = RLdata)
summary(sc2_10RL)
coef(sc2_10RL)
confint(sc2_10RL)
anova(sc2_10RL)
cbind(sc2_10RL, deparse.level = 2)
```

##### CABG + Valve = 3

```{r}
sc3_10RL <- lm(formula = pctCA_PA_systPost10Diff ~ scCABGValve, data = RLdata)
summary(sc3_10RL)
coef(sc3_10RL)
confint(sc3_10RL)
anova(sc3_10RL)
cbind(sc3_10RL, deparse.level = 2)
```

##### Other = 4

```{r}
sc4_10RL <- lm(formula = pctCA_PA_systPost10Diff ~ scOther, data = RLdata)
summary(sc4_10RL)
coef(sc4_10RL)
confint(sc4_10RL)
anova(sc4_10RL)
cbind(sc4_10RL, deparse.level = 2)
```

#### -------------------------------------------

#### Crystalloid Use

```{r}
CrystUse10RL <- lm(formula = pctCA_PA_systPost10Diff ~ crystalloid, data = RLdata)
summary(CrystUse10RL)
coef(CrystUse10RL)
confint(CrystUse10RL)
anova(CrystUse10RL)
cbind(CrystUse10RL, deparse.level = 2)
```

#### PRBC

```{r}
prbc10RL <- lm(formula = pctCA_PA_systPost10Diff ~ prbc, data = RLdata)
summary(prbc10RL)
coef(prbc10RL)
confint(prbc10RL)
anova(prbc10RL)
cbind(prbc10RL, deparse.level = 2)
```

#### Autologous

```{r}
autolgs10RL <- lm(formula = pctCA_PA_systPost10Diff ~ autologous, data = RLdata)
summary(autolgs10RL)
coef(autolgs10RL)
confint(autolgs10RL)
anova(autolgs10RL)
cbind(autolgs10RL, deparse.level = 2)
```

#### Total # Colloid Products 

```{r}
tnColloid10RL <- lm(formula = pctCA_PA_systPost10Diff ~ totnum_colloid, data = RLdata)
summary(tnColloid10RL)
coef(tnColloid10RL)
confint(autolgs10RL)
anova(tnColloid10RL)
cbind(tnColloid10RL, deparse.level = 2)
```

#### Total Colloiod prducts (mls) 

```{r}
tmlsColloid10RL <- lm(formula = pctCA_PA_systPost10Diff ~ totml_colloid, data = RLdata)
summary(tmlsColloid10RL)
coef(tmlsColloid10RL)
confint(tmlsColloid10RL)
anova(tmlsColloid10RL)
cbind(tmlsColloid10RL, deparse.level = 2)
```

#### Cell Saver volume retained

```{r}
csvol10RL <- lm(formula = pctCA_PA_systPost10Diff ~ cellsaver_vol, data = RLdata)
summary(csvol10RL)
coef(csvol10RL)
confint(csvol10RL)
anova(csvol10RL)
cbind(csvol10RL, deparse.level = 2)
```

#### Urine Output

```{r}
urine10RL <- lm(formula = pctCA_PA_systPost10Diff ~ urine, data = RLdata)
summary(urine10RL)
coef(urine10RL)
confint(urine10RL)
anova(urine10RL)
cbind(urine10RL, deparse.level = 2)
```


#### -------------------------------------------

#### CPB duration (min)

```{r}
cpbDur10RL <- lm(formula = pctCA_PA_systPost10Diff ~ cpb_duration, data = RLdata)
summary(cpbDur10RL)
coef(cpbDur10RL)
confint(cpbDur10RL)
anova(cpbDur10RL)
cbind(cpbDur10RL, deparse.level = 2)
```

#### Aortic Clamp time (min)

```{r}
acTime10RL <- lm(formula = pctCA_PA_systPost10Diff ~ aortic_clamp_time, data = RLdata)
summary(acTime10RL)
coef(acTime10RL)
confint(acTime10RL)
anova(acTime10RL)
cbind(acTime10RL, deparse.level = 2)
```

#### Ejection Fraction PRE (%)

```{r}
efPre10RL <- lm(formula = pctCA_PA_systPost10Diff ~ EF_pre, data = RLdata)
summary(efPre10RL)
coef(efPre10RL)
confint(efPre10RL)
anova(efPre10RL)
cbind(efPre10RL, deparse.level = 2)
```

#### Ejection Fraction POST (%)

```{r}
efPost10RL <- lm(formula = pctCA_PA_systPost10Diff ~ EF_post, data = RLdata)
summary(efPost10RL)
coef(efPost10RL)
confint(efPost10RL)
anova(efPost10RL)
cbind(efPost10RL, deparse.level = 2)
```


```{r}
BLdata <- 
  Data %>% 
  filter(Group_char == "BL") %>%
  mutate(syst_pacc_postcpb10 = parse_number(syst_pacc_postcpb10),
    pctCA_PA_systPost2Diff = syst_cacc_postcpb2 - syst_pacc_postcpb2,
    pctCA_PA_systPost10Diff = syst_cacc_postcpb10-syst_pacc_postcpb10)
```

```{r}
RLdata <- 
  Data %>% 
  filter(Group_char == "RL") %>%
  mutate(syst_pacc_postcpb10 = parse_number(syst_pacc_postcpb10),
    pctCA_PA_systPost2Diff = syst_cacc_postcpb2 - syst_pacc_postcpb2,
    pctCA_PA_systPost10Diff = syst_cacc_postcpb10-syst_pacc_postcpb10)
```

```{r}
RSdata <- 
  Data %>% 
  filter(Group_char == "RS") %>%
  mutate(syst_pacc_postcpb10 = parse_number(syst_pacc_postcpb10),
    pctCA_PA_systPost2Diff = syst_cacc_postcpb2 - syst_pacc_postcpb2,
    pctCA_PA_systPost10Diff = syst_cacc_postcpb10-syst_pacc_postcpb10)
```


# Radial Short (RS)

### Post 2 Minutes

#### Age

```{r}
age2RS <- lm(formula = pctCA_PA_systPost2Diff ~ age, data = RSdata)
summary(age2RS)
coef(age2RS)
confint(age2RS)
anova(age2RS)
cbind(age2RS, deparse.level = 2)
```


#### ASA PS

```{r}
asaps2RS <- lm(formula = pctCA_PA_systPost2Diff ~ asaps, data = RSdata)
summary(asaps2RS)
coef(asaps2RS)
confint(asaps2RS)
anova(asaps2RS)
cbind(asaps2RS, deparse.level = 2)
```

#### Male Vs. Female

```{r}
gender2RS <- lm(formula = pctCA_PA_systPost2Diff ~ gender, data = RSdata)
summary(gender2RS)
coef(gender2RS)
confint(gender2RS)
anova(gender2RS)
cbind(gender2RS, deparse.level = 2)
```

#### Weight

```{r}
wght2RS <- lm(formula = pctCA_PA_systPost2Diff ~ weight, data = RSdata)
summary(wght2RS)
coef(wght2RS)
confint(wght2RS)
anova(wght2RS)
cbind(wght2RS, deparse.level = 2)
```

#### Height

```{r}
hght2RS <- lm(formula = pctCA_PA_systPost2Diff ~ height, data = RSdata)
summary(hght2RS)
coef(hght2RS)
confint(hght2RS)
anova(hght2RS)
cbind(hght2RS, deparse.level = 2)
```

#### BMI (Continuous)

```{r}
bmi2RS <- lm(formula = pctCA_PA_systPost2Diff ~ bmi, data = RSdata)
summary(bmi2RS)
coef(bmi2RS)
confint(bmi2RS)
anova(bmi2RS)
cbind(bmi2RS, deparse.level = 2)
```

#### BMI ≥ 35 (binary: Yes=1, No=2)

```{r}
bmi35_2RS <- lm(formula = pctCA_PA_systPost2Diff ~ bmiGE35, data = RSdata)
summary(bmi35_2RS)
coef(bmi35_2RS)
confint(bmi35_2RS)
anova(bmi35_2RS)
cbind(bmi35_2RS, deparse.level = 2)
```

#### BMI ≥ 40 (binary: Yes=1, No=2)

```{r}
bmi40_2RS <- lm(formula = pctCA_PA_systPost2Diff ~ bmiGE40, data = RSdata)
summary(bmi40_2RS)
coef(bmi40_2RS)
confint(bmi40_2RS)
anova(bmi40_2RS)
cbind(bmi40_2RS, deparse.level = 2)
```

#### -------------------------------------------

#### AF

```{r}
af2RS <- lm(formula = pctCA_PA_systPost2Diff ~ af, data = RSdata, family = "binomial")
summary(af2RS)
coef(af2RS)
confint(af2RS)
anova(af2RS)
cbind(af2RS,deparse.level = 2)
```

#### DM

```{r}
dm2RS <- lm(formula = pctCA_PA_systPost2Diff ~ dm, data = RSdata, family = "binomial")
summary(dm2RS)
coef(dm2RS)
confint(dm2RS)
anova(dm2RS)
cbind(dm2RS, deparse.level = 2)
```

#### CKD

```{r}
ckd2RS <- lm(formula = pctCA_PA_systPost2Diff ~ ckd, data = RSdata, family = "binomial")
summary(ckd2RS)
coef(ckd2RS)
confint(ckd2RS)
anova(ckd2RS)
cbind(ckd2RS, deparse.level = 2)
```

#### HTN

```{r}
htn2RS <- lm(formula = pctCA_PA_systPost2Diff ~ htn, data = RSdata)
summary(htn2RS)
coef(htn2RS)
confint(htn2RS)
anova(htn2RS)
cbind(htn2RS, deparse.level = 2)
```

#### COPD

```{r}
copd2RS <- lm(formula = pctCA_PA_systPost2Diff ~ copd, data = RSdata, family = "binomial")
summary(copd2RS)
coef(copd2RS)
confint(copd2RS)
anova(copd2RS)
cbind(copd2RS, deparse.level = 2)
```

#### Hyperlipidemia

```{r}
hyper2RS <- lm(formula = pctCA_PA_systPost2Diff ~ hyperlipid, data = RSdata, family = "binomial")
summary(hyper2RS)
coef(hyper2RS)
confint(hyper2RS)
anova(hyper2RS)
cbind(hyper2RS, deparse.level = 2)
```

#### OSA

```{r}
osa2RS <- lm(formula = pctCA_PA_systPost2Diff ~ osa, data = RSdata)
summary(osa2RS)
coef(osa2RS)
confint(osa2RS)
anova(osa2RS)
cbind(osa2RS, deparse.level = 2)
```

#### PAD

```{r}
pad2RS <- lm(formula = pctCA_PA_systPost2Diff ~ pad, data = RSdata)
summary(pad2RS)
coef(pad2RS)
confint(pad2RS)
anova(pad2RS)
cbind(pad2RS, deparse.level = 2)
```

#### Total (# comorbidities) 

```{r}
tnComorbid2RS <- lm(formula = pctCA_PA_systPost2Diff ~ totnum_comorbid, data = RSdata)
summary(tnComorbid2RS)
coef(tnComorbid2RS)
confint(tnComorbid2RS)
anova(tnComorbid2RS)
cbind(tnComorbid2RS, deparse.level = 2)
```

#### -------------------------------------------

#### Surgical Code (CABG=1, Any Valves =2, CABG+valve=3, Other=4) 

##### CABG = 1

```{r}
sc1_2RS <- lm(formula = pctCA_PA_systPost10Diff ~ scCABG, data = RSdata)
summary(sc1_2RS)
coef(sc1_2RS)
confint(sc1_2RS)
anova(sc1_2RS)
cbind(sc1_2RS, deparse.level = 2)
```

##### Any Valve = 2

```{r}
sc2_2RS <- lm(formula = pctCA_PA_systPost10Diff ~ scAnyValve, data = RSdata)
summary(sc2_2RS)
coef(sc2_2RS)
confint(sc2_2RS)
anova(sc2_2RS)
cbind(sc2_2RS, deparse.level = 2)
```

##### CABG + Valve = 3

```{r}
sc3_2RS <- lm(formula = pctCA_PA_systPost10Diff ~ scCABGValve, data = RSdata)
summary(sc3_2RS)
coef(sc3_2RS)
confint(sc3_2RS)
anova(sc3_2RS)
cbind(sc3_2RS, deparse.level = 2)
```

##### Other = 4

```{r}
sc4_2RS <- lm(formula = pctCA_PA_systPost10Diff ~ scOther, data = RSdata)
summary(sc4_2RS)
coef(sc4_2RS)
confint(sc4_2RS)
anova(sc4_2RS)
cbind(sc4_2RS, deparse.level = 2)
```

#### -------------------------------------------

#### Crystalloid Use

```{r}
CrystUse2RS <- lm(formula = pctCA_PA_systPost2Diff ~ crystalloid, data = RSdata)
summary(CrystUse2RS)
coef(CrystUse2RS)
confint(CrystUse2RS)
anova(CrystUse2RS)
cbind(CrystUse2RS, deparse.level = 2)
```

#### PRBC

```{r}
prbc2RS <- lm(formula = pctCA_PA_systPost2Diff ~ prbc, data = RSdata)
summary(prbc2RS)
coef(prbc2RS)
confint(prbc2RS)
anova(prbc2RS)
cbind(prbc2RS, deparse.level = 2)
```

#### Autologous

```{r}
autolgs2RS <- lm(formula = pctCA_PA_systPost2Diff ~ autologous, data = RSdata)
summary(autolgs2RS)
coef(autolgs2RS)
confint(autolgs2RS)
anova(autolgs2RS)
cbind(autolgs2RS, deparse.level = 2)
```

#### Total # Colloid Products 

```{r}
tnColloid2RS <- lm(formula = pctCA_PA_systPost2Diff ~ totnum_colloid, data = RSdata)
summary(tnColloid2RS)
coef(tnColloid2RS)
confint(tnColloid2RS)
anova(tnColloid2RS)
cbind(tnColloid2RS, deparse.level = 2)
```

#### Total Colloiod prducts (mls) 

```{r}
tmlsColloid2RS <- lm(formula = pctCA_PA_systPost2Diff ~ totml_colloid, data = RSdata)
summary(tmlsColloid2RS)
coef(tmlsColloid2RS)
confint(tmlsColloid2RS)
anova(tmlsColloid2RS)
cbind(tmlsColloid2RS, deparse.level = 2)
```

#### Cell Saver volume retained

```{r}
csvol2RS <- lm(formula = pctCA_PA_systPost2Diff ~ cellsaver_vol, data = RSdata)
summary(csvol2RS)
coef(csvol2RS)
confint(csvol2RS)
anova(csvol2RS)
cbind(csvol2RS, deparse.level = 2)
```

#### Urine Output

```{r}
urine2RS <- lm(formula = pctCA_PA_systPost2Diff ~ urine, data = RSdata)
summary(urine2RS)
coef(urine2RS)
confint(urine2RS)
anova(urine2RS)
cbind(urine2RS, deparse.level = 2)
```


#### -------------------------------------------

#### CPB duration (min)

```{r}
cpbDur2RS <- lm(formula = pctCA_PA_systPost2Diff ~ cpb_duration, data = RSdata)
summary(cpbDur2RS)
coef(cpbDur2RS)
confint(cpbDur2RS)
anova(cpbDur2RS)
cbind(cpbDur2RS, deparse.level = 2)
```

#### Aortic Clamp time (min)

```{r}
acTime2RS <- lm(formula = pctCA_PA_systPost2Diff ~ aortic_clamp_time, data = RSdata)
summary(acTime2RS)
coef(acTime2RS)
confint(acTime2RS)
anova(acTime2RS)
cbind(acTime2RS, deparse.level = 2)
```

#### Ejection Fraction PRE (%)

```{r}
efPre2RS <- lm(formula = pctCA_PA_systPost2Diff ~ EF_pre, data = RSdata)
summary(efPre2RS)
coef(efPre2RS)
confint(efPre2RS)
anova(efPre2RS)
cbind(efPre2RS, deparse.level = 2)
```

#### Ejection Fraction POST (%)

```{r}
efPost2RS <- lm(formula = pctCA_PA_systPost2Diff ~ EF_post, data = RSdata)
summary(efPost2RS)
coef(efPost2RS)
confint(efPost2RS)
anova(efPost2RS)
cbind(efPost2RS, deparse.level = 2)
```


### Post 10 Minutes

#### Age

```{r}
age10RS <- lm(formula = pctCA_PA_systPost10Diff ~ age, data = RSdata)
summary(age10RS)
coef(age10RS)
confint(age10RS)
anova(age10RS)
cbind(age10RS, deparse.level = 2)
```

#### ASA PS

```{r}
asaps10RS <- lm(formula = pctCA_PA_systPost10Diff ~ asaps, data = RSdata)
summary(asaps10RS)
coef(asaps10RS)
confint(asaps10RS)
anova(asaps10RS)
cbind(asaps10RS, deparse.level = 2)
```

#### Male Vs. Female

```{r}
gender10RS <- lm(formula = pctCA_PA_systPost10Diff ~ gender, data = RSdata)
summary(gender10RS)
coef(gender10RS)
confint(gender10RS)
anova(gender10RS)
cbind(gender10RS, deparse.level = 2)
```

#### Weight

```{r}
wght10RS <- lm(formula = pctCA_PA_systPost10Diff ~ weight, data = RSdata)
summary(wght10RS)
coef(wght10RS)
confint(wght10RS)
anova(wght10RS)
cbind(wght10RS, deparse.level = 2)
```

#### Height

```{r}
hght10RS <- lm(formula = pctCA_PA_systPost10Diff ~ height, data = RSdata)
summary(hght10RS)
coef(hght10RS)
confint(hght10RS)
anova(hght10RS)
cbind(hght10RS, deparse.level = 2)
```

#### BMI (Continuous)

```{r}
bmi10RS <- lm(formula = pctCA_PA_systPost10Diff ~ bmi, data = RSdata)
summary(bmi10RS)
coef(bmi10RS)
confint(bmi10RS)
anova(bmi10RS)
cbind(bmi10RS, deparse.level = 2)
```

#### BMI ≥ 35 (binary: Yes=1, No=2)

```{r}
bmi35_10RS <- lm(formula = pctCA_PA_systPost10Diff ~ bmiGE35, data = RSdata)
summary(bmi35_10RS)
coef(bmi35_10RS)
confint(bmi35_10RS)
anova(bmi35_10RS)
cbind(bmi35_10RS, deparse.level = 2)
```

#### BMI ≥ 40 (binary: Yes=1, No=2)

```{r}
bmi40_10RS <- lm(formula = pctCA_PA_systPost10Diff ~ bmiGE40, data = RSdata)
summary(bmi40_10RS)
coef(bmi40_10RS)
confint(bmi40_10RS)
anova(bmi40_10RS)
cbind(bmi40_10RS, deparse.level = 2)
```

#### -------------------------------------------

#### AF

```{r}
af10RS <- lm(formula = pctCA_PA_systPost10Diff ~ af, data = RSdata)
summary(af10RS)
coef(af10RS)
confint(af10RS)
anova(af10RS)
cbind(af10RS, deparse.level = 2)
```

#### DM

```{r}
dm10RS <- lm(formula = pctCA_PA_systPost10Diff ~ dm, data = RSdata)
summary(dm10RS)
coef(dm10RS)
confint(dm10RS)
anova(dm10RS)
cbind(dm10RS, deparse.level = 2)
```

#### CKD

```{r}
ckd10RS <- lm(formula = pctCA_PA_systPost10Diff ~ ckd, data = RSdata)
summary(ckd10RS)
coef(ckd10RS)
confint(ckd10RS)
anova(ckd10RS)
cbind(ckd10RS, deparse.level = 2)
```

#### HTN

```{r}
htn10RS <- lm(formula = pctCA_PA_systPost10Diff ~ htn, data = RSdata)
summary(htn10RS)
coef(htn10RS)
confint(htn10RS)
anova(htn10RS)
cbind(htn10RS, deparse.level = 2)
```

#### COPD

```{r}
copd10RS <- lm(formula = pctCA_PA_systPost10Diff ~ copd, data = RSdata)
summary(copd10RS)
coef(copd10RS)
confint(copd10RS)
anova(copd10RS)
cbind(copd10RS, deparse.level = 2)
```

#### Hyperlipidemia

```{r}
hyper10RS <- lm(formula = pctCA_PA_systPost10Diff ~ hyperlipid, data = RSdata)
summary(hyper10RS)
coef(hyper10RS)
confint(hyper10RS)
anova(hyper10RS)
cbind(hyper10RS, deparse.level = 2)
```

#### OSA

```{r}
osa10RS <- lm(formula = pctCA_PA_systPost10Diff ~ osa, data = RSdata)
summary(osa10RS)
coef(osa10RS)
confint(osa10RS)
anova(osa10RS)
cbind(osa10RS, deparse.level = 2)
```

#### PAD

```{r}
pad10RS <- lm(formula = pctCA_PA_systPost10Diff ~ pad, data = RSdata)
summary(pad10RS)
coef(pad10RS)
confint(pad10RS)
anova(pad10RS)
cbind(pad10RS, deparse.level = 2)
```

#### Total (# comorbidities) 

```{r}
tnComorbid10RS <- lm(formula = pctCA_PA_systPost10Diff ~ totnum_comorbid, data = RSdata)
summary(tnComorbid10RS)
coef(tnComorbid10RS)
confint(tnComorbid10RS)
anova(tnComorbid10RS)
cbind(tnComorbid10RS, deparse.level = 2)
```

#### -------------------------------------------

#### Surgical Code (CABG=1, Any Valves =2, CABG+valve=3, Other=4) 

##### CABG = 1

```{r}
sc1_10RS <- lm(formula = pctCA_PA_systPost10Diff ~ scCABG, data = RSdata)
summary(sc1_10RS)
coef(sc1_10RS)
confint(sc1_10RS)
anova(sc1_10RS)
cbind(sc1_10RS, deparse.level = 2)
```

##### Any Valve = 2

```{r}
sc2_10RS <- lm(formula = pctCA_PA_systPost10Diff ~ scAnyValve, data = RSdata)
summary(sc2_10RS)
coef(sc2_10RS)
confint(sc2_10RS)
anova(sc2_10RS)
cbind(sc2_10RS, deparse.level = 2)
```

##### CABG + Valve = 3

```{r}
sc3_10RS <- lm(formula = pctCA_PA_systPost10Diff ~ scCABGValve, data = RSdata)
summary(sc3_10RS)
coef(sc3_10RS)
confint(sc3_10RS)
anova(sc3_10RS)
cbind(sc3_10RS, deparse.level = 2)
```

##### Other = 4

```{r}
sc4_10RS <- lm(formula = pctCA_PA_systPost10Diff ~ scOther, data = RSdata)
summary(sc4_10RS)
coef(sc4_10RS)
confint(sc4_10RS)
anova(sc4_10RS)
cbind(sc4_10RS, deparse.level = 2)
```

#### -------------------------------------------

#### Crystalloid Use

```{r}
CrystUse10RS <- lm(formula = pctCA_PA_systPost10Diff ~ crystalloid, data = RSdata)
summary(CrystUse10RS)
coef(CrystUse10RS)
confint(CrystUse10RS)
anova(CrystUse10RS)
cbind(CrystUse10RS, deparse.level = 2)
```

#### PRBC

```{r}
prbc10RS <- lm(formula = pctCA_PA_systPost10Diff ~ prbc, data = RSdata)
summary(prbc10RS)
coef(prbc10RS)
confint(prbc10RS)
anova(prbc10RS)
cbind(prbc10RS, deparse.level = 2)
```

#### Autologous

```{r}
autolgs10RS <- lm(formula = pctCA_PA_systPost10Diff ~ autologous, data = RSdata)
summary(autolgs10RS)
coef(autolgs10RS)
confint(autolgs10RS)
anova(autolgs10RS)
cbind(autolgs10RS, deparse.level = 2)
```

#### Total # Colloid Products 

```{r}
tnColloid10RS <- lm(formula = pctCA_PA_systPost10Diff ~ totnum_colloid, data = RSdata)
summary(tnColloid10RS)
coef(tnColloid10RS)
confint(autolgs10RS)
anova(tnColloid10RS)
cbind(tnColloid10RS, deparse.level = 2)
```

#### Total Colloiod prducts (mls) 

```{r}
tmlsColloid10RS <- lm(formula = pctCA_PA_systPost10Diff ~ totml_colloid, data = RSdata)
summary(tmlsColloid10RS)
coef(tmlsColloid10RS)
confint(tmlsColloid10RS)
anova(tmlsColloid10RS)
cbind(tmlsColloid10RS, deparse.level = 2)
```

#### Cell Saver volume retained

```{r}
csvol10RS <- lm(formula = pctCA_PA_systPost10Diff ~ cellsaver_vol, data = RSdata)
summary(csvol10RS)
coef(csvol10RS)
confint(csvol10RS)
anova(csvol10RS)
cbind(csvol10RS, deparse.level = 2)
```

#### Urine Output

```{r}
urine10RS <- lm(formula = pctCA_PA_systPost10Diff ~ urine, data = RSdata)
summary(urine10RS)
coef(urine10RS)
confint(urine10RS)
anova(urine10RS)
cbind(urine10RS, deparse.level = 2)
```


#### -------------------------------------------

#### CPB duration (min)

```{r}
cpbDur10RS <- lm(formula = pctCA_PA_systPost10Diff ~ cpb_duration, data = RSdata)
summary(cpbDur10RS)
coef(cpbDur10RS)
confint(cpbDur10RS)
anova(cpbDur10RS)
cbind(cpbDur10RS, deparse.level = 2)
```

#### Aortic Clamp time (min)

```{r}
acTime10RS <- lm(formula = pctCA_PA_systPost10Diff ~ aortic_clamp_time, data = RSdata)
summary(acTime10RS)
coef(acTime10RS)
confint(acTime10RS)
anova(acTime10RS)
cbind(acTime10RS, deparse.level = 2)
```

#### Ejection Fraction PRE (%)

```{r}
efPre10RS <- lm(formula = pctCA_PA_systPost10Diff ~ EF_pre, data = RSdata)
summary(efPre10RS)
coef(efPre10RS)
confint(efPre10RS)
anova(efPre10RS)
cbind(efPre10RS, deparse.level = 2)
```

#### Ejection Fraction POST (%)

```{r}
efPost10RS <- lm(formula = pctCA_PA_systPost10Diff ~ EF_post, data = RSdata)
summary(efPost10RS)
coef(efPost10RS)
confint(efPost10RS)
anova(efPost10RS)
cbind(efPost10RS, deparse.level = 2)
```




















