---
title: "Radial Short Data"
author: "Matthew Maslow"
date: "2023-07-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

# Packages

```{r}
library(tidyverse)
```

# Read in data

```{r}
data <- read.csv("CSVdata.csv")
colnames(data)
```




# Radial Long (RS)

```{r}
# RS
# n = 68
RSdata <- data %>% filter(Group_char == "RS")
```
```{r}
# readr::write_csv(RSdata, file = "~/Desktop/LifeSpan Data Work/RSdata.csv")
```

### Patient Demo:

###### age
```{r}
ageRS <- 
  RSdata %>% 
  summarise(Mean = mean(age),
            Median = median(age),
            Stan.Dev. = sd(age)
            )
ageRS %>% pander::pander()
```
###### ASA PS

```{r}
asa_psRS <- 
  RSdata %>% 
  summarise(Mean = mean(asaps),
            Median = median(asaps),
            Stan.Dev. = sd(asaps)
            )
asa_psRS %>% pander::pander()
```


###### gender

```{r}

# 1 <- Males
# 2 <- Females

genderRS <- 
  RSdata %>% 
  summarise(Mean = mean(gender),
            Median = median(gender),
            Stan.Dev. = sd(gender)
            )
genderRS %>% pander::pander()
```

###### weight

```{r}
weightRS<-
  RSdata %>%
  summarise(Mean = mean(weight),
            Median = median(weight),
            Stan.Dev. = sd(weight)
            )
weightRS %>% pander::pander()
```

###### height

```{r}
heightRS<-
  RSdata %>%
  summarise(Mean = mean(height),
            Median = median(height),
            Stan.Dev. = sd(height)
            )
heightRS %>% pander::pander()
```

###### bmi

```{r}
bmiRS <- 
  RSdata %>% 
  summarise(Mean = mean(bmi),
            Median = median(bmi),
            Stan.Dev. = sd(bmi)
            )
bmiRS %>% pander::pander()
```

###### bmiGE35

```{r}
bmiGE35RS <- 
  RSdata %>% 
  summarise(Mean = mean(bmiGE35),
            Median = median(bmiGE35),
            Stan.Dev. = sd(bmiGE35)
            )
bmiGE35RS %>% pander::pander()
```

###### bmiGE40

```{r}
bmiGE40RS <- 
  RSdata %>% 
  summarise(Mean = mean(bmiGE40),
            Median = median(bmiGE40),
            Stan.Dev. = sd(bmiGE40)
            )
bmiGE40RS %>% pander::pander()
```


### Prior History:

###### AF

```{r}
afRS <-
  RSdata %>%
  summarise(Mean = mean(af),
            Median = median(af),
            Stan.Dev. = sd(af)
            )
afRS %>% pander::pander()
```

###### DM

```{r}
dmRS <-
  RSdata %>%
  summarise(Mean = mean(dm),
            Median = median(dm),
            Stan.Dev. = sd(dm)
            )
dmRS %>% pander::pander()
```

###### CKD

```{r}
ckdRS <-
  RSdata %>%
  summarise(Mean = mean(ckd),
            Median = median(ckd),
            Stan.Dev. = sd(ckd)
            )
ckdRS %>% pander::pander()
```

###### HTN

```{r}
htnRS <-
  RSdata %>%
  summarise(Mean = mean(htn),
            Median = median(htn),
            Stan.Dev. = sd(htn)
            )
htnRS %>% pander::pander()
```

###### COPD

```{r}
copdRS <-
  RSdata %>%
  summarise(Mean = mean(copd),
            Median = median(copd),
            Stan.Dev. = sd(copd)
            )
copdRS %>% pander::pander()
```

###### Hyperlipidemia

```{r}
hyperlipidRS <-
  RSdata %>% 
  mutate(hyperlipid = parse_number(hyperlipid)) %>%
  summarise(Mean = mean(hyperlipid),
            Median = median(hyperlipid),
            Stan.Dev. = sd(hyperlipid)
            )
hyperlipidRS %>% pander::pander()
```

###### OSA

```{r}
osaRS <-
  RSdata %>%
  summarise(Mean = mean(osa),
            Median = median(osa),
            Stan.Dev. = sd(osa)
            )
osaRS%>% pander::pander()
```

###### PAD

```{r}
padRS <-
  RSdata %>%
  summarise(Mean = mean(pad),
            Median = median(pad),
            Stan.Dev. = sd(pad)
            )
padRS%>% pander::pander()
```

###### Total Num of Comorbidities

```{r}
totnum_comorbidRS <-
  RSdata %>%
  summarise(Mean = mean(totnum_comorbid),
            Median = median(totnum_comorbid),
            Stan.Dev. = sd(totnum_comorbid)
            )
totnum_comorbidRS%>% pander::pander()
```

### Surgery:

###### Group Variables

```{r}
surgeryinfoRS <- 
  RSdata %>% select(surgtype_char, surgtype)
surgeryinfoRS%>% pander::pander()
```

###### Surgery occurences

```{r}
surgFreqRS <- 
  surgeryinfoRS %>%
  summarise(Mean = mean(surgtype),
            Median = median(surgtype),
            Stan.Dev. = sd(surgtype)
            )
surgFreqRS%>% pander::pander()
```

### Intraop FLuids:

###### Crystalloid Use

```{r}
crystalloidRS <- 
  RSdata %>%
  summarise(Mean = mean(crystalloid),
            Median = median(crystalloid),
            Stan.Dev. = sd(crystalloid)
            )
crystalloidRS%>% pander::pander()
```

###### PRBC

```{r}
prbcRS <- 
  RSdata %>%
  summarise(Mean = mean(prbc),
            Median = median(prbc),
            Stan.Dev. = sd(prbc)
            )
prbcRS%>% pander::pander()
```

###### Autologous

```{r}
autologousRS <- 
  RSdata %>%
  summarise(Mean = mean(autologous),
            Median = median(autologous),
            Stan.Dev. = sd(autologous)
            )
autologousRS%>% pander::pander()
```

###### Total Num of Colloid Products

```{r}
totnum_colloidRS <- 
  RSdata %>%
  summarise(Mean = mean(totnum_colloid),
            Median = median(totnum_colloid),
            Stan.Dev. = sd(totnum_colloid)
            )
totnum_colloidRS %>% pander::pander()
```

###### Total Colloid Products (mls)

```{r}
totml_colloidRS <- 
  RSdata %>%
  summarise(Mean = mean(totml_colloid),
            Median = median(totml_colloid),
            Stan.Dev. = sd(totml_colloid)
            )
totml_colloidRS%>% pander::pander()
```

###### Cell Saver Volume Retained

```{r}
cellsaver_volRS <- 
  RSdata %>%
  summarise(Mean = mean(cellsaver_vol),
            Median = median(cellsaver_vol),
            Stan.Dev. = sd(cellsaver_vol)
            )
cellsaver_volRS%>% pander::pander()
```

###### Urine Output

```{r}
urineRS <- 
  RSdata %>%
  summarise(Mean = mean(urine),
            Median = median(urine),
            Stan.Dev. = sd(urine)
            )
urineRS%>% pander::pander()
```

### Surgical Time:

###### CPB duration (min)

```{r}
cpbDurationRS <-
  RSdata %>%
  summarise(Mean = mean(cpb_duration),
            Median = median(cpb_duration),
            Stan.Dev. = sd(cpb_duration)
            )
cpbDurationRS%>% pander::pander()
  
```

###### Aortic Clamp time (min)

```{r}
aortic_clamp_timeRS <-
  RSdata %>%
  summarise(Mean = mean(aortic_clamp_time),
            Median = median(aortic_clamp_time),
            Stan.Dev. = sd(aortic_clamp_time)
            )
aortic_clamp_timeRS%>% pander::pander()
```

###### Ejection Fraction PRE (%)

```{r}
ef_preRS <-
  RSdata %>%
  mutate(EF_pre = parse_number(EF_pre)) %>%
  summarise(Mean = mean(EF_pre,na.rm = TRUE),
            Median = median(EF_pre, na.rm = TRUE),
            Stan.Dev. = sd(EF_pre, na.rm = TRUE)
            )
ef_preRS%>% pander::pander()
```

###### Ejection Fraction POST (%)

```{r}
ef_postRS <-
  RSdata %>%
  mutate(EF_post = parse_number(EF_post)) %>%
  summarise(Mean = mean(EF_post,na.rm = TRUE),
            Median = median(EF_post, na.rm = TRUE),
            Stan.Dev. = sd(EF_post, na.rm = TRUE)
            )
ef_postRS%>% pander::pander()
```

### Intra-Operative Meds:

###### IntraOp Norepinephrine

```{r}
intra_norepRS <- 
  RSdata %>%
  summarise(Mean = mean(Intra_norep),
            Median = median(Intra_norep),
            Stan.Dev. = sd(Intra_norep)
            )
intra_norepRS%>% pander::pander()
```

###### IntraOp Nitroglycerin

```{r}
intra_nitroRS <- 
  RSdata %>%
  summarise(Mean = mean(intra_nitro),
            Median = median(intra_nitro),
            Stan.Dev. = sd(intra_nitro)
            )
intra_nitroRS%>% pander::pander()
```

###### IntraOp Vasopressin

```{r}
intra_vasoRS <- 
  RSdata %>%
  summarise(Mean = mean(intra_vaso),
            Median = median(intra_vaso),
            Stan.Dev. = sd(intra_vaso)
            )
intra_vasoRS%>% pander::pander()
```

###### IntraOp Milrinone

```{r}
intra_milRS <- 
  RSdata %>%
  summarise(Mean = mean(intra_mil),
            Median = median(intra_mil),
            Stan.Dev. = sd(intra_mil)
            )
intra_milRS%>% pander::pander()
```

###### IntraOp Epinephrine

```{r}
intra_epiRS <- 
  RSdata %>%
  summarise(Mean = mean(intra_epi),
            Median = median(intra_epi),
            Stan.Dev. = sd(intra_epi)
            )
intra_epiRS%>% pander::pander()
```

###### IntraOp Phenylephrine

```{r}
intra_phenylRS <- 
  RSdata %>%
  summarise(Mean = mean(intra_phenyl),
            Median = median(intra_phenyl),
            Stan.Dev. = sd(intra_phenyl)
            )
intra_phenylRS%>% pander::pander()
```

### Post Bypass Meds:

###### IntraOp Norepinephrine

```{r}
intraPost_norepRS <- 
  RSdata %>%
  summarise(Mean = mean(post_norep),
            Median = median(post_norep),
            Stan.Dev. = sd(post_norep)
            )
intraPost_norepRS%>% pander::pander()
```

###### IntraOp Nitroglycerin

```{r}
intraPost_nitroRS <- 
  RSdata %>%
  summarise(Mean = mean(post_nitro),
            Median = median(post_nitro),
            Stan.Dev. = sd(post_nitro)
            )
intraPost_nitroRS%>% pander::pander()
```

###### IntraOp Vasopressin

```{r}
intraPost_vasoRS <- 
  RSdata %>%
  summarise(Mean = mean(post_vaso),
            Median = median(post_vaso),
            Stan.Dev. = sd(post_vaso)
            )
intraPost_vasoRS%>% pander::pander()
```

###### IntraOp Milrinone

```{r}
intraPost_milRS <- 
  RSdata %>%
  summarise(Mean = mean(post_mil),
            Median = median(post_mil),
            Stan.Dev. = sd(post_mil)
            )
intraPost_milRS%>% pander::pander()
```

###### IntraOp Epinephrine

```{r}
intraPost_epiRS <- 
  RSdata %>%
  summarise(Mean = mean(post_epi),
            Median = median(post_epi),
            Stan.Dev. = sd(post_epi)
            )
intraPost_epiRS%>% pander::pander()
```

###### IntraOp Phenylephrine

```{r}
intraPost_phenylRS <- 
  RSdata %>%
  summarise(Mean = mean(post_phenyl),
            Median = median(post_phenyl),
            Stan.Dev. = sd(post_phenyl)
            )
intraPost_phenylRS%>% pander::pander()
```

### Central Aortic Cannula Pressures:

###### syst_cacc_precpb

```{r}
caccSYSTpreRS <-
  RSdata %>% 
  summarise(Mean = mean(syst_cacc_precpb,na.rm = TRUE),
            Median = median(syst_cacc_precpb,na.rm = TRUE),
            Standard_Deviation = sd(syst_cacc_precpb,na.rm = TRUE)
            )
caccSYSTpreRS%>% pander::pander()
```


###### map_cacc_precpb

```{r}
caccMAPpreRS <- 
  RSdata %>% 
  summarise(Mean = mean(map_pacc_precpb,na.rm = TRUE),
            Median = median(map_cacc_precpb,na.rm = TRUE),
            Standard_Deviation = sd(map_cacc_precpb,na.rm = TRUE)
            )
caccMAPpreRS%>% pander::pander()
```

###### syst_cacc_postcpb2

```{r}
caccSystTWOpostRS <- 
  RSdata %>%
  summarise(Mean = mean(syst_cacc_postcpb2, na.rm = TRUE),
            Median = median(syst_cacc_postcpb2, na.rm = TRUE),
            Standard_Deviation = sd(syst_cacc_postcpb2,na.rm = TRUE)
            )
caccSystTWOpostRS%>% pander::pander()
```

###### map_cacc_postcpb2

```{r}
caccMapTWOpostRS <- 
  RSdata %>%
  summarise(Mean = mean(map_cacc_postcpb2, na.rm = TRUE),
            Median = median(map_cacc_postcpb2, na.rm = TRUE),
            Standard_Deviation = sd(map_cacc_postcpb2,na.rm = TRUE)
            )
caccMapTWOpostRS%>% pander::pander()
```

###### syst_cacc_postcpb10

```{r}
caccSystTENpostRS <- 
  RSdata %>%
  summarise(Mean = mean(syst_cacc_postcpb10, na.rm = TRUE),
            Median = median(syst_cacc_postcpb10, na.rm = TRUE),
            Standard_Deviation = sd(syst_cacc_postcpb10,na.rm = TRUE)
            )
caccSystTENpostRS%>% pander::pander()
```

###### map_cacc_postcpb10

```{r}
caccMapTENpostRS <- 
  RSdata %>%
  summarise(Mean = mean(map_cacc_postcpb10, na.rm = TRUE),
            Median = median(map_cacc_postcpb10, na.rm = TRUE),
            Standard_Deviation = sd(map_cacc_postcpb10,na.rm = TRUE)
            )
caccMapTENpostRS%>% pander::pander()
```


### Peripheral Arterial Catheter Pressures:

#### First Time Frame: Pre

###### syst_pacc_precpb

```{r}
paccSYSTpreRS <- 
  RSdata %>% 
  summarise(Mean = mean(syst_pacc_precpb,na.rm = TRUE),
            Median = median(syst_pacc_precpb,na.rm = TRUE),
            Stan.Dev. = sd(syst_pacc_precpb,na.rm = TRUE)
            )
paccSYSTpreRS%>% pander::pander()
```

###### map_pacc_precpb

```{r}
paccMAPpreRS <- 
  RSdata %>% 
  summarise(Mean = mean(map_pacc_precpb,na.rm = TRUE),
            Median = median(map_pacc_precpb,na.rm = TRUE),
            Standard_Deviation = sd(map_pacc_precpb,na.rm = TRUE)
            )
paccMAPpreRS%>% pander::pander()
```

###### diast_pacc_precpb

```{r}
paccDIASTpreRS <- 
  RSdata %>% 
  mutate(diast_pacc_precpb = parse_number(diast_pacc_precpb)) %>%
  summarise(Mean = mean(diast_pacc_precpb,na.rm = TRUE),
            Median = median(diast_pacc_precpb,na.rm = TRUE),
            Standard_Deviation = sd(diast_pacc_precpb,na.rm = TRUE)
            )
paccDIASTpreRS%>% pander::pander()
BLdata$wave_pacc_precpb
```

###### wave_pacc_precpb

```{r}
paccWAVEpreRS <- 
  RSdata %>% 
  summarise(Mean = mean(wave_pacc_precpb,na.rm = TRUE),
            Median = median(wave_pacc_precpb,na.rm = TRUE),
            Standard_Deviation = sd(wave_pacc_precpb,na.rm = TRUE)
            )
paccWAVEpreRS%>% pander::pander()
```





#### Second Time Frame: 2-Min-Post:

###### syst_pacc_postcpb2

```{r}
paccSystTWOpostRS <- 
  RSdata %>%
  summarise(Mean = mean(syst_pacc_postcpb2, na.rm = TRUE),
            Median = median(syst_pacc_postcpb2, na.rm = TRUE),
            Standard_Deviation = sd(syst_pacc_postcpb2,na.rm = TRUE)
            )
paccSystTWOpostRS%>% pander::pander()
```

###### map_pacc_postcpb2

```{r}
paccMapTWOpostRS <- 
  RSdata %>%
  summarise(Mean = mean(map_pacc_postcpb2, na.rm = TRUE),
            Median = median(map_pacc_postcpb2, na.rm = TRUE),
            Standard_Deviation = sd(map_pacc_postcpb2,na.rm = TRUE)
            )
paccMapTWOpostRS%>% pander::pander()
```

###### wave_pacc_postcpb2

```{r}
paccWaveTWOpostRS <- 
  RSdata %>%
  summarise(Mean = mean(wave_pacc_postcpb2, na.rm = TRUE),
            Median = median(wave_pacc_postcpb2, na.rm = TRUE),
            Standard_Deviation = sd(wave_pacc_postcpb2,na.rm = TRUE)
            )
paccWaveTWOpostRS%>% pander::pander()
```



#### Third Time Frame: 10-Min-Post:

###### syst_pacc_postcpb10

```{r}
paccSystTENpostRS <- 
  RSdata %>% 
  mutate(syst_pacc_postcpb10 = parse_number(syst_pacc_postcpb10)) %>%
  summarise(Mean = mean(syst_pacc_postcpb10, na.rm = TRUE),
            Median = median(syst_pacc_postcpb10, na.rm = TRUE),
            Standard_Deviation = sd(syst_pacc_postcpb10,na.rm = TRUE)
            )
paccSystTENpostRS%>% pander::pander()
```

###### map_pacc_postcpb10

```{r}
paccMapTENpostRS <- 
  RSdata %>% 
  mutate(map_pacc_postcpb10 = parse_number(map_pacc_postcpb10)) %>%
  summarise(Mean = mean(map_pacc_postcpb10, na.rm = TRUE),
            Median = median(map_pacc_postcpb10, na.rm = TRUE),
            Standard_Deviation = sd(map_pacc_postcpb10,na.rm = TRUE)
            )
paccMapTENpostRS%>% pander::pander()
```

###### wave_pacc_postcpb10

```{r}
paccWaveTENpostRS <- 
  RSdata %>% 
  mutate(wave_pacc_postcpb10 = parse_number(wave_pacc_postcpb10)) %>%
  summarise(Mean = mean(wave_pacc_postcpb10, na.rm = TRUE),
            Median = median(wave_pacc_postcpb10, na.rm = TRUE),
            Standard_Deviation = sd(wave_pacc_postcpb10,na.rm = TRUE)
            )
paccWaveTENpostRS%>% pander::pander()
```




#### CICU:

###### syst_pacc_cicu

```{r}
paccSYSTcicuRS <- 
  RSdata %>% 
  mutate(syst_pacc_cicu = parse_number(syst_pacc_cicu)) %>%
  summarise(Mean = mean(syst_pacc_cicu, na.rm = TRUE),
            Median = median(syst_pacc_cicu, na.rm = TRUE),
            Standard_Deviation = sd(syst_pacc_cicu,na.rm = TRUE)
            )
paccSYSTcicuRS%>% pander::pander()
```

###### diast_pacc_cicu

```{r}
paccDIASTcicuRS <- 
  RSdata %>% 
  mutate(diast_pacc_cicu = parse_number(diast_pacc_cicu)) %>%
  summarise(Mean = mean(diast_pacc_cicu, na.rm = TRUE),
            Median = median(diast_pacc_cicu, na.rm = TRUE),
            Standard_Deviation = sd(diast_pacc_cicu,na.rm = TRUE)
            )
paccDIASTcicuRS%>% pander::pander()
```

###### map_pacc_cicu

```{r}
paccMAPcicuRS <- 
  RSdata %>% 
  mutate(map_pacc_cicu = parse_number(map_pacc_cicu)) %>%
  summarise(Mean = mean(map_pacc_cicu, na.rm = TRUE),
            Median = median(map_pacc_cicu, na.rm = TRUE),
            Standard_Deviation = sd(map_pacc_cicu,na.rm = TRUE)
            )
paccMAPcicuRS%>% pander::pander()
```

###### wave_pacc_cicu

```{r}
paccWAVEcicuRS <- 
  RSdata %>% 
  mutate(wave_pacc_cicu = parse_number(wave_pacc_cicu)) %>%
  summarise(Mean = mean(wave_pacc_cicu, na.rm = TRUE),
            Median = median(wave_pacc_cicu, na.rm = TRUE),
            Standard_Deviation = sd(wave_pacc_cicu,na.rm = TRUE)
            )
paccWAVEcicuRS%>% pander::pander()
```








