---
title: "Radial Long Data"
author: "Matthew Maslow"
date: "2023-07-02"
output: html_document 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```


# Packages

```{r}
library(tidyverse)
```


# Read in data

```{r}
data <- read.csv("CSVdata.csv")
colnames(data)
```




# Radial Long (RL)

```{r}
# RL
# n = 63
RLdata <- data %>% filter(Group_char == "RL")
RLdata%>% pander::pander()
```
```{r}
# readr::write_csv(RLdata, file = "~/Desktop/LifeSpan Data Work/RLdata.csv")
```

### Patient Demo:

###### age
```{r}
ageRL <- 
  RLdata %>% 
  summarise(Mean = mean(age),
            Median = median(age),
            Stan.Dev. = sd(age)
            )
ageRL %>% pander::pander()
```

###### ASA PS

```{r}
asa_psRL <- 
  RSdata %>% 
  summarise(Mean = mean(asaps),
            Median = median(asaps),
            Stan.Dev. = sd(asaps)
            )
asa_psRL %>% pander::pander()
```

###### gender

```{r}

# 1 <- Males
# 2 <- Females

genderRL <- 
  RLdata %>% 
  summarise(Mean = mean(gender),
            Median = median(gender),
            Stan.Dev. = sd(gender)
            )
genderRL%>% pander::pander()
```

###### weight

```{r}
weightRL<-
  RLdata %>%
  summarise(Mean = mean(weight),
            Median = median(weight),
            Stan.Dev. = sd(weight)
            )
weightRL %>% pander::pander()
```

###### height

```{r}
heightRL<-
  RLdata %>%
  summarise(Mean = mean(height),
            Median = median(height),
            Stan.Dev. = sd(height)
            )
heightRL %>% pander::pander()
```

###### bmi

```{r}
bmiRL <- 
  RLdata %>% 
  summarise(Mean = mean(bmi),
            Median = median(bmi),
            Stan.Dev. = sd(bmi)
            )
bmiRL %>% pander::pander()
```

###### bmiGE35

```{r}
bmiGE35RL <- 
  RLdata %>% 
  summarise(Mean = mean(bmiGE35),
            Median = median(bmiGE35),
            Stan.Dev. = sd(bmiGE35)
            )
bmiGE35RL %>% pander::pander()
```

###### bmiGE40

```{r}
bmiGE40RL <- 
  RLdata %>% 
  summarise(Mean = mean(bmiGE40),
            Median = median(bmiGE40),
            Stan.Dev. = sd(bmiGE40)
            )
bmiGE40RL %>% pander::pander()
```


### Prior History:

###### AF

```{r}
afRL <-
  RLdata %>%
  summarise(Mean = mean(af),
            Median = median(af),
            Stan.Dev. = sd(af)
            )
afRL %>% pander::pander()
```

###### DM

```{r}
dmRL <-
  RLdata %>%
  summarise(Mean = mean(dm),
            Median = median(dm),
            Stan.Dev. = sd(dm)
            )
dmRL %>% pander::pander()
```

###### CKD

```{r}
ckdRL <-
  RLdata %>%
  summarise(Mean = mean(ckd),
            Median = median(ckd),
            Stan.Dev. = sd(ckd)
            )
ckdRL %>% pander::pander()
```

###### HTN

```{r}
htnRL <-
  RLdata %>%
  summarise(Mean = mean(htn),
            Median = median(htn),
            Stan.Dev. = sd(htn)
            )
htnRL %>% pander::pander()
```

###### COPD

```{r}
copdRL <-
  RLdata %>%
  summarise(Mean = mean(copd),
            Median = median(copd),
            Stan.Dev. = sd(copd)
            )
copdRL %>% pander::pander()
```

###### Hyperlipidemia

```{r}
hyperlipidRL <-
  RLdata %>% 
  mutate(hyperlipid = parse_number(hyperlipid)) %>%
  summarise(Mean = mean(hyperlipid),
            Median = median(hyperlipid),
            Stan.Dev. = sd(hyperlipid)
            )
hyperlipidRL %>% pander::pander()
```

###### OSA

```{r}
osaRL <-
  RLdata %>%
  summarise(Mean = mean(osa),
            Median = median(osa),
            Stan.Dev. = sd(osa)
            )
osaRL %>% pander::pander()
```

###### PAD

```{r}
padRL <-
  RLdata %>%
  summarise(Mean = mean(pad),
            Median = median(pad),
            Stan.Dev. = sd(pad)
            )
padRL %>% pander::pander()
```

###### Total Num of Comorbidities

```{r}
totnum_comorbidRL <-
  RLdata %>%
  summarise(Mean = mean(totnum_comorbid),
            Median = median(totnum_comorbid),
            Stan.Dev. = sd(totnum_comorbid)
            )
totnum_comorbidRL %>% pander::pander()
```

### Surgery:

###### Group Variables

```{r}
surgeryinfoRL <- 
  RLdata %>% select(surgtype_char, surgtype)
surgeryinfoRL
```

###### Surgery occurences

```{r}
surgFreqRL <- 
  surgeryinfoRL %>%
  summarise(Mean = mean(surgtype),
            Median = median(surgtype),
            Stan.Dev. = sd(surgtype)
            )
surgFreqRL
```

### Intraop FLuids:

###### Crystalloid Use

```{r}
crystalloidRL <- 
  RLdata %>%
  summarise(Mean = mean(crystalloid),
            Median = median(crystalloid),
            Stan.Dev. = sd(crystalloid)
            )
crystalloidRL
```

###### PRBC

```{r}
prbcRL <- 
  RLdata %>%
  summarise(Mean = mean(prbc),
            Median = median(prbc),
            Stan.Dev. = sd(prbc)
            )
prbcRL
```

###### Autologous

```{r}
autologousRL <- 
  RLdata %>%
  summarise(Mean = mean(autologous),
            Median = median(autologous),
            Stan.Dev. = sd(autologous)
            )
autologousRL
```

###### Total Num of Colloid Products

```{r}
totnum_colloidRL <- 
  RLdata %>%
  summarise(Mean = mean(totnum_colloid),
            Median = median(totnum_colloid),
            Stan.Dev. = sd(totnum_colloid)
            )
totnum_colloidRL %>% pander::pander()
```

###### Total Colloid Products (mls)

```{r}
totml_colloidRL <- 
  RLdata %>%
  summarise(Mean = mean(totml_colloid),
            Median = median(totml_colloid),
            Stan.Dev. = sd(totml_colloid)
            )
totml_colloidRL%>% pander::pander()
```

###### Cell Saver Volume Retained

```{r}
cellsaver_volRL <- 
  RLdata %>%
  summarise(Mean = mean(cellsaver_vol),
            Median = median(cellsaver_vol),
            Stan.Dev. = sd(cellsaver_vol)
            )
cellsaver_volRL%>% pander::pander()
```

###### Urine Output

```{r}
urineRL <- 
  RLdata %>%
  summarise(Mean = mean(urine),
            Median = median(urine),
            Stan.Dev. = sd(urine)
            )
urineRL%>% pander::pander()
```

### Surgical Time:

###### CPB duration (min)

```{r}
cpbDurationRL <-
  RLdata %>%
  summarise(Mean = mean(cpb_duration),
            Median = median(cpb_duration),
            Stan.Dev. = sd(cpb_duration)
            )
cpbDurationRL%>% pander::pander()
  
```

###### Aortic Clamp time (min)

```{r}
aortic_clamp_timeRL <-
  RLdata %>%
  summarise(Mean = mean(aortic_clamp_time),
            Median = median(aortic_clamp_time),
            Stan.Dev. = sd(aortic_clamp_time)
            )
aortic_clamp_timeRL%>% pander::pander()
```

###### Ejection Fraction PRE (%)

```{r}
ef_preRL <-
  RLdata %>%
  mutate(EF_pre = parse_number(EF_pre)) %>%
  summarise(Mean = mean(EF_pre,na.rm = TRUE),
            Median = median(EF_pre, na.rm = TRUE),
            Stan.Dev. = sd(EF_pre, na.rm = TRUE)
            )
ef_preRL%>% pander::pander()
```

###### Ejection Fraction POST (%)

```{r}
ef_postRL <-
  RLdata %>%
  mutate(EF_post = parse_number(EF_post)) %>%
  summarise(Mean = mean(EF_post,na.rm = TRUE),
            Median = median(EF_post, na.rm = TRUE),
            Stan.Dev. = sd(EF_post, na.rm = TRUE)
            )
ef_postRL%>% pander::pander()
```

### Intra-Operative Meds:

###### IntraOp Norepinephrine

```{r}
intra_norepRL <- 
  RLdata %>%
  summarise(Mean = mean(Intra_norep),
            Median = median(Intra_norep),
            Stan.Dev. = sd(Intra_norep)
            )
intra_norepRL%>% pander::pander()
```

###### IntraOp Nitroglycerin

```{r}
intra_nitroRL <- 
  RLdata %>%
  summarise(Mean = mean(intra_nitro),
            Median = median(intra_nitro),
            Stan.Dev. = sd(intra_nitro)
            )
intra_nitroRL%>% pander::pander()
```

###### IntraOp Vasopressin

```{r}
intra_vasoRL <- 
  RLdata %>%
  summarise(Mean = mean(intra_vaso),
            Median = median(intra_vaso),
            Stan.Dev. = sd(intra_vaso)
            )
intra_vasoRL%>% pander::pander()
```

###### IntraOp Milrinone

```{r}
intra_milRL <- 
  RLdata %>%
  summarise(Mean = mean(intra_mil),
            Median = median(intra_mil),
            Stan.Dev. = sd(intra_mil)
            )
intra_milRL%>% pander::pander()
```

###### IntraOp Epinephrine

```{r}
intra_epiRL <- 
  RLdata %>%
  summarise(Mean = mean(intra_epi),
            Median = median(intra_epi),
            Stan.Dev. = sd(intra_epi)
            )
intra_epiRL%>% pander::pander()
```

###### IntraOp Phenylephrine

```{r}
intra_phenylRL <- 
  RLdata %>%
  summarise(Mean = mean(intra_phenyl),
            Median = median(intra_phenyl),
            Stan.Dev. = sd(intra_phenyl)
            )
intra_phenylRL%>% pander::pander()
```

### Post Bypass Meds:

###### IntraOp Norepinephrine

```{r}
intraPost_norepRL <- 
  RLdata %>%
  summarise(Mean = mean(post_norep),
            Median = median(post_norep),
            Stan.Dev. = sd(post_norep)
            )
intraPost_norepRL%>% pander::pander()
```

###### IntraOp Nitroglycerin

```{r}
intraPost_nitroRL <- 
  RLdata %>%
  summarise(Mean = mean(post_nitro),
            Median = median(post_nitro),
            Stan.Dev. = sd(post_nitro)
            )
intraPost_nitroRL%>% pander::pander()
```

###### IntraOp Vasopressin

```{r}
intraPost_vasoRL <- 
  RLdata %>%
  summarise(Mean = mean(post_vaso),
            Median = median(post_vaso),
            Stan.Dev. = sd(post_vaso)
            )
intraPost_vasoRL%>% pander::pander()
```

###### IntraOp Milrinone

```{r}
intraPost_milRL <- 
  RLdata %>%
  summarise(Mean = mean(post_mil),
            Median = median(post_mil),
            Stan.Dev. = sd(post_mil)
            )
intraPost_milRL%>% pander::pander()
```

###### IntraOp Epinephrine

```{r}
intraPost_epiRL <- 
  RLdata %>%
  summarise(Mean = mean(post_epi),
            Median = median(post_epi),
            Stan.Dev. = sd(post_epi)
            )
intraPost_epiRL%>% pander::pander()
```

###### IntraOp Phenylephrine

```{r}
intraPost_phenylRL <- 
  RLdata %>%
  summarise(Mean = mean(post_phenyl),
            Median = median(post_phenyl),
            Stan.Dev. = sd(post_phenyl)
            )
intraPost_phenylRL%>% pander::pander()
```

### Central Aortic Cannula Pressures:

###### syst_cacc_precpb

```{r}
caccSYSTpreRL <-
  RLdata %>% 
  summarise(Mean = mean(syst_cacc_precpb,na.rm = TRUE),
            Median = median(syst_cacc_precpb,na.rm = TRUE),
            Standard_Deviation = sd(syst_cacc_precpb,na.rm = TRUE)
            )
caccSYSTpreRL%>% pander::pander()
```


###### map_cacc_precpb

```{r}
caccMAPpreRL <- 
  RLdata %>% 
  summarise(Mean = mean(map_pacc_precpb,na.rm = TRUE),
            Median = median(map_cacc_precpb,na.rm = TRUE),
            Standard_Deviation = sd(map_cacc_precpb,na.rm = TRUE)
            )
caccMAPpreRL%>% pander::pander()
```

###### syst_cacc_postcpb2

```{r}
caccSystTWOpostRL <- 
  RLdata %>%
  summarise(Mean = mean(syst_cacc_postcpb2, na.rm = TRUE),
            Median = median(syst_cacc_postcpb2, na.rm = TRUE),
            Standard_Deviation = sd(syst_cacc_postcpb2,na.rm = TRUE)
            )
caccSystTWOpostRL%>% pander::pander()
```

###### map_cacc_postcpb2

```{r}
caccMapTWOpostRL <- 
  RLdata %>%
  summarise(Mean = mean(map_cacc_postcpb2, na.rm = TRUE),
            Median = median(map_cacc_postcpb2, na.rm = TRUE),
            Standard_Deviation = sd(map_cacc_postcpb2,na.rm = TRUE)
            )
caccMapTWOpostRL%>% pander::pander()
```

###### syst_cacc_postcpb10

```{r}
caccSystTENpostRL <- 
  RLdata %>%
  summarise(Mean = mean(syst_cacc_postcpb10, na.rm = TRUE),
            Median = median(syst_cacc_postcpb10, na.rm = TRUE),
            Standard_Deviation = sd(syst_cacc_postcpb10,na.rm = TRUE)
            )
caccSystTENpostRL%>% pander::pander()
```

###### map_cacc_postcpb10

```{r}
caccMapTENpostRL <- 
  RLdata %>%
  summarise(Mean = mean(map_cacc_postcpb10, na.rm = TRUE),
            Median = median(map_cacc_postcpb10, na.rm = TRUE),
            Standard_Deviation = sd(map_cacc_postcpb10,na.rm = TRUE)
            )
caccMapTENpostRL%>% pander::pander()
```


### Peripheral Arterial Catheter Pressures:

#### First Time Frame: Pre

###### syst_pacc_precpb

```{r}
paccSYSTpreRL <- 
  RLdata %>% 
  summarise(Mean = mean(syst_pacc_precpb,na.rm = TRUE),
            Median = median(syst_pacc_precpb,na.rm = TRUE),
            Stan.Dev. = sd(syst_pacc_precpb,na.rm = TRUE)
            )
paccSYSTpreRL%>% pander::pander()
```

###### map_pacc_precpb

```{r}
paccMAPpreRL <- 
  RLdata %>% 
  summarise(Mean = mean(map_pacc_precpb,na.rm = TRUE),
            Median = median(map_pacc_precpb,na.rm = TRUE),
            Standard_Deviation = sd(map_pacc_precpb,na.rm = TRUE)
            )
paccMAPpreRL%>% pander::pander()
```

###### diast_pacc_precpb

```{r}
paccDIASTpreRL <- 
  RLdata %>% 
  mutate(diast_pacc_precpb = parse_number(diast_pacc_precpb)) %>%
  summarise(Mean = mean(diast_pacc_precpb,na.rm = TRUE),
            Median = median(diast_pacc_precpb,na.rm = TRUE),
            Standard_Deviation = sd(diast_pacc_precpb,na.rm = TRUE)
            )
paccDIASTpreRL%>% pander::pander()
```

###### wave_pacc_precpb

```{r}
paccWAVEpreRL <- 
  RLdata %>% 
  summarise(Mean = mean(wave_pacc_precpb,na.rm = TRUE),
            Median = median(wave_pacc_precpb,na.rm = TRUE),
            Standard_Deviation = sd(wave_pacc_precpb,na.rm = TRUE)
            )
paccWAVEpreRL%>% pander::pander()
```





#### Second Time Frame: 2-Min-Post:

###### syst_pacc_postcpb2

```{r}
paccSystTWOpostRL <- 
  RLdata %>%
  summarise(Mean = mean(syst_pacc_postcpb2, na.rm = TRUE),
            Median = median(syst_pacc_postcpb2, na.rm = TRUE),
            Standard_Deviation = sd(syst_pacc_postcpb2,na.rm = TRUE)
            )
paccSystTWOpostRL%>% pander::pander()
```

###### map_pacc_postcpb2

```{r}
paccMapTWOpostRL <- 
  RLdata %>%
  summarise(Mean = mean(map_pacc_postcpb2, na.rm = TRUE),
            Median = median(map_pacc_postcpb2, na.rm = TRUE),
            Standard_Deviation = sd(map_pacc_postcpb2,na.rm = TRUE)
            )
paccMapTWOpostRL%>% pander::pander()
```

###### wave_pacc_postcpb2

```{r}
paccWaveTWOpostRL <- 
  RLdata %>%
  summarise(Mean = mean(wave_pacc_postcpb2, na.rm = TRUE),
            Median = median(wave_pacc_postcpb2, na.rm = TRUE),
            Standard_Deviation = sd(wave_pacc_postcpb2,na.rm = TRUE)
            )
paccWaveTWOpostRL%>% pander::pander()
```



#### Third Time Frame: 10-Min-Post:

###### syst_pacc_postcpb10

```{r}
paccSystTENpostRL <- 
  RLdata %>% 
  mutate(syst_pacc_postcpb10 = parse_number(syst_pacc_postcpb10)) %>%
  summarise(Mean = mean(syst_pacc_postcpb10, na.rm = TRUE),
            Median = median(syst_pacc_postcpb10, na.rm = TRUE),
            Standard_Deviation = sd(syst_pacc_postcpb10,na.rm = TRUE)
            )
paccSystTENpostRL%>% pander::pander()
```

###### map_pacc_postcpb10

```{r}
paccMapTENpostRL <- 
  RLdata %>% 
  mutate(map_pacc_postcpb10 = parse_number(map_pacc_postcpb10)) %>%
  summarise(Mean = mean(map_pacc_postcpb10, na.rm = TRUE),
            Median = median(map_pacc_postcpb10, na.rm = TRUE),
            Standard_Deviation = sd(map_pacc_postcpb10,na.rm = TRUE)
            )
paccMapTENpostRL%>% pander::pander()
```

###### wave_pacc_postcpb10

```{r}
paccWaveTENpostRL <- 
  RLdata %>% 
  mutate(wave_pacc_postcpb10 = parse_number(wave_pacc_postcpb10)) %>%
  summarise(Mean = mean(wave_pacc_postcpb10, na.rm = TRUE),
            Median = median(wave_pacc_postcpb10, na.rm = TRUE),
            Standard_Deviation = sd(wave_pacc_postcpb10,na.rm = TRUE)
            )
paccWaveTENpostRL%>% pander::pander()
```




#### CICU:

###### syst_pacc_cicu

```{r}
paccSYSTcicuRL <- 
  RLdata %>% 
  mutate(syst_pacc_cicu = parse_number(syst_pacc_cicu)) %>%
  summarise(Mean = mean(syst_pacc_cicu, na.rm = TRUE),
            Median = median(syst_pacc_cicu, na.rm = TRUE),
            Standard_Deviation = sd(syst_pacc_cicu,na.rm = TRUE)
            )
paccSYSTcicuRL%>% pander::pander()
```

###### diast_pacc_cicu

```{r}
paccDIASTcicuRL <- 
  RLdata %>% 
  mutate(diast_pacc_cicu = parse_number(diast_pacc_cicu)) %>%
  summarise(Mean = mean(diast_pacc_cicu, na.rm = TRUE),
            Median = median(diast_pacc_cicu, na.rm = TRUE),
            Standard_Deviation = sd(diast_pacc_cicu,na.rm = TRUE)
            )
paccDIASTcicuRL%>% pander::pander()
```

###### map_pacc_cicu

```{r}
paccMAPcicuRL <- 
  RLdata %>% 
  mutate(map_pacc_cicu = parse_number(map_pacc_cicu)) %>%
  summarise(Mean = mean(map_pacc_cicu, na.rm = TRUE),
            Median = median(map_pacc_cicu, na.rm = TRUE),
            Standard_Deviation = sd(map_pacc_cicu,na.rm = TRUE)
            )
paccMAPcicuRL%>% pander::pander()
```

###### wave_pacc_cicu

```{r}
paccWAVEcicuRL <- 
  RLdata %>% 
  mutate(wave_pacc_cicu = parse_number(wave_pacc_cicu)) %>%
  summarise(Mean = mean(wave_pacc_cicu, na.rm = TRUE),
            Median = median(wave_pacc_cicu, na.rm = TRUE),
            Standard_Deviation = sd(wave_pacc_cicu,na.rm = TRUE)
            )
paccWAVEcicuRL%>% pander::pander()
```











