---
title: "Bootstrap Confidence Intervals"
author: "Stat 326 (Chapman)"
date: "3/14/2023"
output: word_document
---

## Bootstrap for a Population Mean
The number of hours of exercise per week for a random sample of Stat 113 students are provided.
```{r}
data = c(12,3,4,10,8,17,15,5,8,10,8,25,1,15,2,14,10,8,6,14,5,6,12,3)

hist(data)
mean(data)


n=length(data)
means = NULL
B = 1000

for (i in 1:B)
{
	boot_sample = sample(data,n,replace=T)
	boot_mean = mean(boot_sample)
	means = c(means, boot_mean)
}

hist(means,col="medium sea green")
abline(v=mean(data),col="red",lwd=2)

# mean of bootstrap distribution (should be close to our statistic)
mean(means)

# 90% CI
quantile(means,c(0.05, 0.95))

# 95% CI
quantile(means,c(0.025, 0.975))

```


## Bootstrap for a Population Proportion
In a random sample of 588 adults, 16.67% reported that key lime pie is their favorite kind of pie. Construct a 95% Bootstrap percentile confidence interval that have key lime as their favorite pie.
```{r}
data = c( rep(1, round(588*.1667)), rep(0, 588-round(588*.1667)))
n=length(data)
props = NULL
B = 5000







hist(props,col="medium sea green")
abline(v=mean(data),col="red",lwd=2)

# center of bootstrap distribution (should be close to our sample statistic)
mean(props)

# 90% CI
quantile(props,c(0.05, 0.95))

# 95% CI
quantile(props,c(0.025, 0.975))

```


## Bootstrap for Two Samples
```{r}
sampleNo=c(6,2,5,6,10,2,14,4,6,0,4,5,1,5,8,8,10,14,5,10,7,9)
sampleYes=c(7,20,12,5,18,7,15,18,13,0,8,7,12,12,20,13,16)

n1 = length(sampleNo)
n2 = length(sampleYes)

mean(sampleYes) - mean(sampleNo) # our sample statistic (diff. in means)
mean(sampleYes)/mean(sampleNo) # our sample statistic (ratio of means)

diffs = NULL
ratios = NULL
B = 5000







par(mfrow=c(1,2))
hist(diffs,col="medium sea green")
abline(v=(mean(sampleYes) - mean(sampleNo)),col="red",lwd=2)
hist(ratios, col="light sea green")
abline(v=mean(sampleYes)/mean(sampleNo),col="red",lwd=2)

# mean of the bootstrap distribution of diffs
mean(diffs)
# mean of the bootstrap distribution of diffs
mean(ratios)

# 90% CI diffs
quantile(diffs,c(0.05, 0.95))

# 90% CI ratios
quantile(ratios,c(0.05, 0.95))

```


