---
title: "HW6 - MattMaslow"
author: "Matthew Maslow"
date: "3/27/2023"
output:
  word_document: default
  html_document: default
---
#### Packages:
```{r message=FALSE, warning=FALSE}
library(resampledata)
library(dplyr)
library(ggplot2)
```

## 7.6

#### 12.

###### a.

```{r}
data("Girls2004")
```
```{r}
smoke <- 
  Girls2004 %>% filter(
    Smoker == "Yes"
  ) %>% 
  ggplot(smoke, mapping = aes(Weight) ) +
  geom_histogram(col="black") +
  labs(title = "Smokes") + theme_light()

noSmoke <- Girls2004 %>% filter(
  Smoker == "No"
       )  %>% 
  ggplot(noSmoke, mapping = aes(Weight) ) +
  geom_histogram(col = "black") +
  labs(title = "Doesn't Smoke") + theme_light()

smoke
noSmoke
```

###### b.

```{r}
# 95% CI for lower bound of the diff in means of baby weights of
#   smokes vs. non-smokers
NSbar = mean(noSmoke$data$Weight)
Smkbar = mean(smoke$data$Weight)
sNS = sd(noSmoke$data$Weight)
sSmk = sd(smoke$data$Weight)
(df = ( (sNS^2/ 69)^2 + (sSmk^2 / 11)^2 ) / ( ( ( (sNS^2/ 69)^2) / 68 + (sSmk^2 / 11)^2 / 10) ) )
t = -2.218
result = (NSbar - Smkbar) + (t) * (sqrt( (sNS^2/69) + (sSmk^2/11) ) )
result
```

We are 95% confident the that the lower bound of the mean difference of baby
weights of non-smokers versus smokers is -56.11419 grams.

#### 13.

```{r}
data(Spruce)
```

###### a.

```{r}
fertilized <- 
  Spruce %>% filter(
    Fertilizer == "F"
  ) %>% 
  ggplot(fertilized, mapping = aes(Ht.change) ) +
  geom_density(col = "darkgreen")+
  labs(title = "Fertilized" ) + theme_light()

nonFertilized <- 
  Spruce %>% filter(
    Fertilizer == "NF"
  ) %>% 
  ggplot(nonFertilized, mapping = aes(Ht.change) ) +
  geom_density(col = "darkgreen")+
  labs(title = "Not Fertilized") + theme_light()

fertilized
nonFertilized
```

###### b.

```{r}
# 95% CI for the lower bound of the diff in mean height change for the Spruces
FertBar <- mean(fertilized$data$Ht.change)
nonFertBar <- mean(nonFertilized$data$Ht.change)
sFert <- sd(fertilized$data$Ht.change)
sNonFert <- sd(nonFertilized$data$Ht.change)
(df = ( (sFert^2/ 36)^2 + (sNonFert^2 / 36)^2 ) / ( ( ( (sFert^2/ 36)^2) / 35 + (sNonFert^2 / 36)^2 / 35) ) )
t = -2.030
answer = (FertBar - nonFertBar) + (t) * (sqrt( (sFert^2/36) + (sNonFert^2/36) ) )
answer
```

We are 95% confident that the lower bound of the mean difference between Spruces
with fertilizer versus without is 10.76 feet.

## 5.6:

#### 12.

```{r}
data("FishMercury")
```

###### a.

```{r}
fmPlot <-
  FishMercury %>%
  ggplot(aes(Mercury)) +
  geom_dotplot(col = "darkblue") +
  labs(title = "Mercury Content in Fish")
fmPlot
```

Most of the data on the fishes are located under 0.25mg, then there is an outlier
that is above 1.75mg.

###### b.

```{r}
hist(FishMercury$Mercury)
mean(FishMercury$Mercury)


n=length(FishMercury$Mercury)
means = NULL
B = 1000

for (i in 1:B)
{
	boot_sample = sample(FishMercury$Mercury,n,replace=T)
	boot_mean = mean(boot_sample)
	means = c(means, boot_mean)
}

hist(means,col="green")
abline(v=mean(FishMercury$Mercury),col="red",lwd=2)

# mean of bootstrap distribution (should be close to our statistic)
mean(means)
sd(boot_sample)

# 95% CI
quantile(means,c(0.025, 0.975))

```

$Bootstrap mean = 0.1821461$ $Bootstrap StandErr = 0.3221959$ 
Bootstrap percentile interval for 95% is $(0.1133625,0.3060025)$

###### c.

```{r}
newFishMercury <-
  FishMercury %>%
  filter(Mercury < 1)
```
```{r}
hist(newFishMercury$Mercury)
mean(newFishMercury$Mercury)


n=length(newFishMercury$Mercury)
means = NULL
B = 1000

for (i in 1:B)
{
	boot_sample = sample(newFishMercury$Mercury,n,replace=T)
	boot_mean = mean(boot_sample)
	means = c(means, boot_mean)
}

hist(means,col="green")
abline(v=mean(newFishMercury$Mercury),col="red",lwd=2)

# mean of bootstrap distribution (should be close to our statistic)
mean(means)
sd(boot_sample)

# 95% CI
quantile(means,c(0.025, 0.975))

```

Bootstrap percentile interval for 95% without the outlier is...
$(0.1080681, 0.1400698)$

###### d.

By removing the outlier it significantly improved the distribution of data.
The mean of the data is now centered in the histogram, which also has a normal
shape now, where the original was skewed. Also, looking at 95% bootstrap 
interval it narrowed the width of bounds.












