---
title: "Permutation Tests"
author: "Stat 326 (Chapman)"
date: "3/30/2023 or 4/4/2023"
output: word_document
---

Permutation Test example 1: A subset of the "Flight Data"
```{r}
library(tidyverse)
library(resampledata)
data("FlightDelays")# this dataset is quite large, and I want a small sample of it for class
set.seed(4445557)
FDclass = slice_sample(FlightDelays, n=50) %>% 
  select(Carrier, Delay)
```

Understand our data
```{r}
# "Explore" data
FDclass %>% 
  ggplot(aes(x=Carrier,y=Delay,fill=Carrier)) + 
  geom_boxplot()
# summary statistics
FDclass %>%
  group_by(Carrier) %>%
  summarize(n=n(),
            mean=mean(Delay))
```

Code for Permutation Test: Difference in Pop means for carriers
```{r}
# From our summary statistics
AA = FDclass %>% filter(Carrier == "AA") %>% select(Delay)
AA = AA$Delay
UA = FDclass %>% filter(Carrier == "UA") %>% select(Delay)
UA = UA$Delay
teststat = round(mean(AA) - mean(UA),2) # AA Sample mean - UA Sample mean

nA = length(AA)  # these are important
nU = length(UA)  # these are important

nulldist = NULL   # an object to store our teststats under the null hypothesis
nPerm = 5000        # number of permutation samples

for (i in 1:nPerm)
{
  onepop = c(AA,UA) # Under Ho, there is really only one population
  
  AAind = sample(1:(nA+nU),nA)  # there are nA+nU flights in our population;
                                # random pick nA of them to arbitrarily label as "AA"
                                # note that this code picks indices between 1 and nA+nU
  arbAA = onepop[AAind]    # pull the chosen flights out of the pop and arbitrarily call AA
  arbUA = onepop[-AAind]  # pull the remaining flights from the pop and arbitrarily call UA
  
  dstar = mean(arbAA) - mean(arbUA)
  nulldist[i] = dstar
}

# visualize our null distribution
hist(nulldist,col="mediumseagreen", xlab="Distribution of xbar-ybar under Ho of 'One Pop'")
# visualize our test statistic on the null distribution
abline(v=teststat,col="red",lwd=2)

# "conservative" p-value ("+1" represents our original sample; avoids p-value=0)
# if Ha: mu_AA > mu_UA
(sum(nulldist > teststat)+1)/(nPerm+1)

# if Ha: mu_AA not equal mu_UA
2*(sum(nulldist > teststat)+1)/(nPerm+1)

```

Example 2: Spruce

In the Black Spruce Case Study in Section 1.9, seedlings were planted in plots that were
either subject to competition (from other plants) or not. Use the data set Spruce to conduct a test to see if there is evidence that the mean growth ("Ht.change") differs for the two treatments (C = Competition or NC = No Competition).

```{r}
data("Spruce")
```


```{r}

```

