---
title: "Sampling Distribution Simulation"
author: "Stat 326 (Chapman)"
date: "1/19/2023"
output:
  word_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---

### Starting a Simulation 

1. Choose a population model for the simulation. 

  Let's start with Normal($\mu$=10, $\sigma^2$=4).

2. Choose a sample size for the simulation.

  Let's start with $n$=5.
  
3. Choose a calculation for the simulation.

  Let's start with the sample mean, $\bar{x}$.


### Look at what happens when we do this one time

Carefully look through this code and output to understand the process of generating a sample from a population and computing a statistic.
```{r CHUNK1}

n = 5       # sample size
mu = 10     # population mean
sigma = 2   # population standard deviation

# generate a random sample of n observations from population
my.sample = round(rnorm(n, mu, sigma ),2)  
# look at the sample
my.sample   

# compute the sample mean
my.mean = mean(my.sample)
# look at the sample mean
my.mean     


## visualize all of the above simultaneously

# generate a range of values that span the population
xvals = seq(mu-4*sigma, mu+4*sigma, by=0.1)   

# plot the normal density curve over the above range 
plot(xvals, dnorm(xvals, mu, sigma), type="l")

# plot the n sample points
points(my.sample,rep(0,n), pch=19)

# plot the sample mean
abline(v=my.mean,col="red", lwd=2)          
```
  
### Repeat process a large number of times
```{r CHUNK2}

n = 5            # sample size
mu = 10          # population mean
sigma = 2        # population standard deviation
nsim = 5000      # number of simulations

# the following code allocates space to save the results for each of our simulated values
my.means = numeric(nsim)   

for (i in 1:nsim) # loop through the iterations in the simulation
{
  my.sample = round(rnorm(n, mu, sigma ), 2)
  my.means[i] = mean(my.sample) 
}

# summarize the simulation results
hist(my.means, main=paste("Sampling Distribution of the \n Sample Mean when n =",n))
mean(my.means)
var(my.means)

# What is the probability that we observe a sample mean larger than 11?
mean(my.means>11)

# What is the probability that we observe a sample mean less than or equal to 9.5?
mean(my.means<=9.5)


```

### Discussion Questions
 
1. Run CHUNK2 several times. How do the results change (or not)? 
2. What can we conclude about the sampling distribution of $\bar{x}$ when taking samples of $n=5$ from _this_ population? 
3. How do the simulation results compare to the result from Stat 325?
```{r CHUNK3}
hist(my.means, main=paste("Sampling Distribution of the \n Sample Mean when n =",n),freq=FALSE)
lines(xvals, dnorm(xvals, mu, sigma/sqrt(n)),col="blue",lwd=2)
```

4. Increase the sample size in CHUNK2 and rerun CHUNK2 and CHUNK3. How do the results (mean, standard deviation, and probabilities) change? Do the changes make sense?

### Consider a non-Normal population

Now consider an Exponential(0.5) population. Go back to a sample size of $n=5$ and continue calculating the sample mean, $\bar{x}$.

5. In CHUNK4, I modified the CHUNK1 code to do all of the same things as CHUNK1 (examine a single sample from the known population), but for an Exponential population. What are some changes I made and why?


```{r CHUNK4}

n = 5       # sample size
lambda = 0.5
mu = 1/lambda   # population mean
sigma = sqrt(1/lambda^2)  # population standard deviation

# generate a random sample of n observations from population
my.sample = round(rexp(n, lambda),2)  
# look at the sample
my.sample   

# compute the sample mean
my.mean = mean(my.sample)
# look at the sample mean
my.mean     


## visualize all of the above simultaneously

# generate a range of values that span the population
xvals = seq(0,4.5*sigma, by=0.1)   

# plot the normal density curve over the above range 
plot(xvals, dexp(xvals, lambda), type="l")

# plot the n sample points
points(my.sample,rep(0,n), pch=19)

# plot the sample mean
abline(v=my.mean,col="red", lwd=2)          
```

6. Run CHUNK5 (below) to explore the sampling distribution of $\bar{x}$ when the population is Exponential and the sample size is $n=5$. Summarize what you notice about the sampling distribution of $\bar{x}$ when taking a sample of size $n=5$ from an Exponential(0.5) population.


```{r CHUNK5}

n = 5       # sample size
lambda = 0.5
mu = 1/lambda   # population mean
sigma = sqrt(1/lambda^2)  # population standard deviation

# the following code allocates space to save the results for each of our simulated values
my.means = numeric(nsim)   

for (i in 1:nsim) # loop through the iterations in the simulation
{
  my.sample = round(rexp(n, lambda), 2)
  my.means[i] = mean(my.sample) 
}

# summarize the simulation results
hist(my.means, main=paste("Sampling Distribution of the \n Sample Mean when n =",n),freq=FALSE)
mean(my.means)
var(my.means)

``` 




7. Increase the sample size in CHUNK5 to $n=50$. What do you notice about the sampling distribution of $\bar{x}$ now? What is this called?


8. In general, what are some other ways you could summarize a sample of data? (i.e., other calculations you could do?)



## Repeat above for the sample minimum

Copy CHUNK1 and paste it below (rename it CHUNK6). Change the statistic calculated to be the sample minimum. Run CHUNK6 a few times so that you understand our problem.


9. PREDICT WHAT MIGHT HAPPEN NEXT: Based on what you've seen by rerunning CHUNK6. Where do you expect the center of the sampling distribution of the sample minimum to be relative to 10?

Copy CHUNK2 and paste it below (rename it CHUNK7). Change the statistic calculated to be the sample minimum. Run CHUNK7 to explore the sampling distribution of the sample minimum. 


10. Summarize what you notice about the sampling distribution. How does it compare to the sampling distribution of the sample mean? Does that make sense? Why or why not?


11. Report the probability that the sample minimum is less than or equal to 9.5. How does it compare to the probability that the sample mean is less than or equal to 9.5? Does that make sense? Why or why not?

12. Increase the sample size to 50. Summarize how the sampling distribution of the sample minimum when $n=50$ differs from when $n=5$.
